---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# Planned Updates

* None at this time.

# Version History

## v0.1.0.9003
2017-06-05

* SSD function, non-functional at this point
    + raw data
    + Process raw data script
    + data_SSD.rda in data folder
    + SSD function script
    + data.R, add description of data
* Remove hello function
* Add CoOccur function.
    + raw data
    + process raw data script
    + data_CoOccur in data folder
    + CoOccur script
    + data.R, add description of data

## v0.1.0.9002
2017-05-27

* Knit README.RMD so README.md will display on GitHub.

## v0.1.0.9001
2017-05-27

* Added basic package structure.
    + Folders (data, data-raw, inst/doc, inst/extdata, man, R, vignettes)
    + NEWS, README
* Update DESCRIPTION, NEWS, and README

## v0.1.0
2017-05-27

* Initial commit on GitHub.

