---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# Planned Updates

* None at this time.

# Future Updates

* CoOccur function.
    + Add scoring to 2nd set of plots.
    + Retain scoring from both sets of plots in a table.
    
* Convert site map to ggplot.

* input file data.SSTV.totabund for the function getStressorSpecificRegressions.

* Scores to files

* Hightlight "better" bio sites

* StreamCat data.  Boxplots with jitter points.

# Version History

## Changes in Version 0.1.0.9039 (2017-06-20)

* Rename 2 functions with "get" to match others.
    + CoOccur
    + SSD
    + Update vignette.

## Changes in Version 0.1.0.9038 (2017-06-20)

* Update examples.  Issue #5.
    + getStressorSpecificRegressions
    + Use BMIRelAbund.rda for data.SSTV.totabund
    + Replace BenSampID with BMI.Metrics.SampID
    + Not finished.  Not working.
* Add data file; BMIRelAbund.rda
    + Include in data-raw and Data.R
    + Data for data.SSTV.totabund in getStressorSpecificRegressions.

## Changes in Version 0.1.0.9037 (2017-06-16)

* Update examples.  Issue #5.
    + getAlgStressorReponses
    
## Changes in Version 0.1.0.9036 (2017-06-16)

* Update examples.  Issue #5.
    + getAlgMatches

## Changes in Version 0.1.0.9035 (2017-06-16)

* Update examples.  Issue #5.
    + getStressorSpecificRegressions
    + Need input file data.SSTV.totabund

## Changes in Version 0.1.0.9034 (2017-06-15)

* Update examples.  Issue #5.
    + getBMIStressorResponses

## Changes in Version 0.1.0.9033 (2017-06-15)

* Update examples.  Issue #5.
    + getBMImatches

## Changes in Version 0.1.0.9032 (2017-06-15)

* Update examples.  Issue #5.
    + getClusterInfo

## Changes in Version 0.1.0.9031 (2017-06-15)

* Update examples.  Issue #5.
    + getStressorList
* Add subdir check to functions that use "Results" subdire.
    + getSiteInfo
    + getChemDataSubsets
    + getStressorList
    + getClusterInfo
    + getAlgStressorResponses
    + getBMIStressorResponses
    + getStressorSpecificRegressions

## Changes in Version 0.1.0.9030 (2017-06-15)

* Update examples.  Issue #5.
    + getChemDataSubsets
* Update data.R.
    + data_Chem
    + data_ChemInfo (update data with GroupName)
    + data_Cluster_Hi

## Changes in Version 0.1.0.9029 (2017-06-15)

* Add vignette.
    + Add package `imager` to Suggests in DESCRIPTION.
    + Basic outline.
    + getSiteInfo function.

## Changes in Version 0.1.0.9028 (2017-06-14)

* GIS data.
    + Standardize projection for GIS layers.
    + getSiteInfo; modify plot and projection used for layers.
* getSiteInfo
    + modify "cluster" data column.
* Examples, change clustertype "H6" to "5"
    + getAlgMatches
    + getAlgStressorResponse
    + getBMIMatches
    + getBMIStressorResponses
    + getCheDataSubsests
    + getClsuterInfo
    + getSiteInfo
    + getStressorList
    + getStressorSpecificRegressions
* data_Sites
    + Modify reference to match code.

## Changes in Version 0.1.0.9027 (2017-06-14)

* Add GIS data.
    + data.R
    + data_GIS_Flow_HI
    + data_GIS_Flow_LO
    + data_GIS_AZ_Outline
* Update getSiteInfo map.
    + Uncomment map code.
    + Change graphics::plot to sp::plot.
* Revised data_SampSummary.
* Revise SampIDs in other files to match format in SampSummary.
    + data_AlgMetrics
    + data_BMIcounts
    + data_BMIMetrics
    + data_Chem

## Changes in Version 0.1.0.9026 (2017-06-12)

* Add data_BMIcounts.
    + Update data.R.
    + Update getStressorSpecificRegressions example.

## Changes in Version 0.1.0.9025 (2017-06-12)

* Modify examples for TargetSite and getSiteInfo.  Issue #5
    + getAlgmatches, getAlgStressorResponses, getBMImatches, getBMIStressorResponses
    , getClusterInfo, getStressorList, getStressorSpecificRegressions.
* Modify examples for file imports vs. included datasets.  Issue #5
    + getAlgmatches, getBMImatches, getClusterInfo, getStressorSpecificRegressions

## Changes in Version 0.1.0.9024 (2017-06-12)

* getChemDataSubset
    + default useLU to FALSE.
    + Error if no cluster information.   Added "stop" condition.

## Changes in Version 0.1.0.9023 (2017-06-11)

* Update example in getChemDataSubset. Issue #5.
    + Create data_ChemInfo
    + Create data_Chem
    + Remove "dontrun" in example.

## Changes in Version 0.1.0.9022 (2017-06-11)

* Add AZ data to "data-raw" and "data". Issue #5.
* getSiteInfo.R
    + Add example datasets (include description in data.R)
    + Turn off mapping.
    + Turn off "donotrun" in example.

## Changes in Version 0.1.0.9021 (2017-06-08)

* Add data requirements to "get" functions in the "details" section.
    + Include column names for required imports
* Add helper function getRegPlotSet.
* Add examples but mark as "dont' run".  Issue #5.
* Add function getAlgMatches.
    + Include return value.

## Changes in Version 0.1.0.9020 (2017-06-07)

* SSDplot
    + Add 3rd dataset so can QC against USEPA ssd generator Excel file.
    + Change proportion formula; rank-0.05 to rank-0.5 to match USEPA
    + Change "Species" to "Taxa" in 2 locations in the code.

## Changes in Version 0.1.0.9019 (2017-06-07)

* Modify format of NEWS file.  Issue #1.

## Changes in Version 0.1.0.9018 (2017-06-06)

* Check issues addressed:
    + Depends R >= 2.1.0
    + no visible global function definition (multiple)
    + Add to Imports; graphics, grDevices, stats, utils
* Check issues not addressed:
    + data_CoOccur, non-ASCII characters in column names.
    + Undocumented object "cluster" in getChemDataSubsets
    + no visible binding for global variable (multiple)
* SSDplot
    + Add second dataset and example.
    + Modify text; font size and justification

## Changes in Version 0.1.0.9017 (2017-06-06)

* Update functions for package dependencies, e.g., readOGR to rgdal::readOGR.
    + getSiteInfo; rgdal
    + getChemDataSubsets; reshape
    + getStressorList; dplyr

## Changes in Version 0.1.0.9016 (2017-06-06)

* Rename SSD function to SSDplot due to conflict with stats::SSD.
* Update CASTfxn.R for function name change.

## Changes in Version 0.1.0.9015 (2017-06-06)

* Fix StressorList return value.  Issue #2.

## Changes in Version 0.1.0.9014 (2017-06-06)

* Fix SSD function.  Issue #3.

## Changes in Version 0.1.0.9013 (2017-06-06)

* Add CASTfxn.R so the package has a help file.

## Changes in Version 0.1.0.9012 (2017-06-06)

* Add function getStressorSpecificRegressions.

## Changes in Version 0.1.0.9011 (2017-06-06)

* Add function getAlgStressorResponses.

## Changes in Version 0.1.0.9010 (2017-06-06)

* Add function getBMIStressorResponses.

## Changes in Version 0.1.0.9009 (2017-06-06)

* Add function getBMImatches.

## Changes in Version 0.1.0.9008 (2017-06-06)

* Add function getStressorList.

## Changes in Version 0.1.0.9007 (2017-06-06)

* Add function getClusterInfo.
* SSD.R
    + Remove "conf=0.95" from qnorm function.

## Changes in Version 0.1.0.9006 (2017-06-06)

* Add function getChemDataSubsets.

## Changes in Version 0.1.0.9005 (2017-06-06)

* Add function getSiteInfo.
* Add Imports to DESCRIPTION.
    + maps
    + maptools
    + raster
    + RColorBrewer
    + reshape
    + rgdal
    + rgeos
    + RgoogleMaps

## Changes in Version 0.1.0.9004 (2017-06-06)

* CoOccur function.
    + Update example.  Remove 2nd Stressors line.
    + Update details from Sue Norton presentation 2017-06-05.

## Changes in Version 0.1.0.9003 (2017-06-05)

* SSD function, non-functional at this point
    + raw data
    + Process raw data script
    + data_SSD.rda in data folder
    + SSD function script
    + data.R, add description of data
* Remove hello function
* Add CoOccur function.
    + raw data
    + process raw data script
    + data_CoOccur in data folder
    + CoOccur script
    + data.R, add description of data

## Changes in Version 0.1.0.9002 (2017-05-27)

* Knit README.RMD so README.md will display on GitHub.

## Changes in Version 0.1.0.9001 (2017-05-27)

* Added basic package structure.
    + Folders (data, data-raw, inst/doc, inst/extdata, man, R, vignettes)
    + NEWS, README
* Update DESCRIPTION, NEWS, and README

## Changes in Version 0.1.0 (2017-05-27)

* Initial commit on GitHub.

