---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# Planned Updates

* None at this time.

* CoOccur function.
    + Add scoring to 2nd set of plots.
    + Retain scoring from both sets of plots in a table.

* Functions from Ann
    + getSiteInfo (summary info including lat/long, ref status, cluster membership, samps from site, maps)
    + getChemDataSubsets (summary information about chems)
    + getClusterInfo (summary cluster information)
    + getStressorID (box plots of each stressor, grouped by category)
    + getBMImatches (matched chem/bmi samples)
    + getAlgMatches (matched chem/algal samples)
    + getBMIstressorResponses (regressions)
    + getAlgStressorResponses (regressions)
    + getStressorSpecificRegressions (%Fines)
    + getSSDs (pesticides, metals)

# Version History

## v0.1.0.9005
2017-06-06

* Add function getSiteInfo.
* Add Imports to DESCRIPTION.
    + maps
    + maptools
    + raster
    + RColorBrewer
    + reshape
    + rgdal
    + rgeos
    + RgoogleMaps

## v0.1.0.9004
2017-06-06

* CoOccur function.
    + Update example.  Remove 2nd Stressors line.
    + Update details from Sue Norton presentation 2017-06-05.

## v0.1.0.9003
2017-06-05

* SSD function, non-functional at this point
    + raw data
    + Process raw data script
    + data_SSD.rda in data folder
    + SSD function script
    + data.R, add description of data
* Remove hello function
* Add CoOccur function.
    + raw data
    + process raw data script
    + data_CoOccur in data folder
    + CoOccur script
    + data.R, add description of data

## v0.1.0.9002
2017-05-27

* Knit README.RMD so README.md will display on GitHub.

## v0.1.0.9001
2017-05-27

* Added basic package structure.
    + Folders (data, data-raw, inst/doc, inst/extdata, man, R, vignettes)
    + NEWS, README
* Update DESCRIPTION, NEWS, and README

## v0.1.0
2017-05-27

* Initial commit on GitHub.

