---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# Planned Updates

* None at this time.

* CoOccur function.
    + Add scoring to 2nd set of plots.
    + Retain scoring from both sets of plots in a table.

# Version History

## Changes in Version 0.1.0.9019 (2017-06-07)

* Modify format of NEWS file.  Issue #1.

## Changes in Version 0.1.0.9018 (2017-06-06)

* Check issues addressed:
    + Depends R >= 2.1.0
    + no visible global function definition (multiple)
    + Add to Imports; graphics, grDevices, stats, utils
* Check issues not addressed:
    + data_CoOccur, non-ASCII characters in column names.
    + Undocumented object "cluster" in getChemDataSubsets
    + no visible binding for global variable (multiple)
* SSDplot
    + Add second dataset and example.
    + Modify text; font size and justification

## Changes in Version 0.1.0.9017 (2017-06-06)

* Update functions for package dependencies, e.g., readOGR to rgdal::readOGR.
    + getSiteInfo; rgdal
    + getChemDataSubsets; reshape
    + getStressorList; dplyr

## Changes in Version 0.1.0.9016 (2017-06-06)

* Rename SSD function to SSDplot due to conflict with stats::SSD.
* Update CASTfxn.R for function name change.

## Changes in Version 0.1.0.9015 (2017-06-06)

* Fix StressorList return value.  Issue #2.

## Changes in Version 0.1.0.9014 (2017-06-06)

* Fix SSD function.  Issue #3.

## Changes in Version 0.1.0.9013 (2017-06-06)

* Add CASTfxn.R so the package has a help file.

## Changes in Version 0.1.0.9012 (2017-06-06)

* Add function getStressorSpecificRegressions.

## Changes in Version 0.1.0.9011 (2017-06-06)

* Add function getAlgStressorResponses.

## Changes in Version 0.1.0.9010 (2017-06-06)

* Add function getBMIStressorResponses.

## Changes in Version 0.1.0.9009 (2017-06-06)

* Add function getBMImatches.

## Changes in Version 0.1.0.9008 (2017-06-06)

* Add function getStressorList.

## Changes in Version 0.1.0.9007 (2017-06-06)

* Add function getClusterInfo.
* SSD.R
    + Remove "conf=0.95" from qnorm function.

## Changes in Version 0.1.0.9006 (2017-06-06)

* Add function getChemDataSubsets.

## Changes in Version 0.1.0.9005 (2017-06-06)

* Add function getSiteInfo.
* Add Imports to DESCRIPTION.
    + maps
    + maptools
    + raster
    + RColorBrewer
    + reshape
    + rgdal
    + rgeos
    + RgoogleMaps

## Changes in Version 0.1.0.9004 (2017-06-06)

* CoOccur function.
    + Update example.  Remove 2nd Stressors line.
    + Update details from Sue Norton presentation 2017-06-05.

## Changes in Version 0.1.0.9003 (2017-06-05)

* SSD function, non-functional at this point
    + raw data
    + Process raw data script
    + data_SSD.rda in data folder
    + SSD function script
    + data.R, add description of data
* Remove hello function
* Add CoOccur function.
    + raw data
    + process raw data script
    + data_CoOccur in data folder
    + CoOccur script
    + data.R, add description of data

## Changes in Version 0.1.0.9002 (2017-05-27)

* Knit README.RMD so README.md will display on GitHub.

## Changes in Version 0.1.0.9001 (2017-05-27)

* Added basic package structure.
    + Folders (data, data-raw, inst/doc, inst/extdata, man, R, vignettes)
    + NEWS, README
* Update DESCRIPTION, NEWS, and README

## Changes in Version 0.1.0 (2017-05-27)

* Initial commit on GitHub.

