---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# Planned Updates

* None at this time.

# Future Updates

* Convert site map to ggplot.

* input file data.SSTV.totabund for the function getStressorSpecificRegressions.

* StreamCat data.  Boxplots with jitter points.

* getBioStressorResponses
    + Add stressor response plot from getCoOccur

# Version History

## Changes in Version 0.1.0.9288 (2020-09-14)
* getSiteInfo.R
    + Add dir_map_rmd as input parameter.

## Changes in Version 0.1.0.9287 (2020-09-14)
* RPPTool
    + Update server.R with skeleton code revisions.
    + Update other function files.
    + Keep all inputs on single tab.
    + Turn off stressor weights.
    + Ensure all functions in /external are sourced in global.R
    + Add data/BCG_ProportionalOdds_20200113.xlsx
    + external directory, Copy RMD from inst/rmd
        - Map_Leaflet.rmd
* CASTool
    + Data/SMCClusterInfo.tab, updated version.
    + external directory, Copy RMD from inst/rmd
        - Report_Results_overall.rmd
        - Report_Results_summary.rmd

## Changes in Version 0.1.0.9286 (2020-09-10)
* RPPTool
    + RPPTool_CA.R, Add Shiny code.
    + Add sourced scripts.
    + server.R
        - Add in skeleton code.
* DESCRIPTION
    + Add lubridate
* Add Data/NHDPlusNetwork.xlsx

## Changes in Version 0.1.0.9285 (2020-09-10)
* RPPTool
   + global.R
       - Change read statement directory for rda files

## Changes in Version 0.1.0.9284 (2020-09-10)
* RPPTool
   + global.R
       - Change read statement for SMCSitesFinal to work on shinyapps.io.

## Changes in Version 0.1.0.9283 (2020-09-09)
* CASTool
    + server.R
        - Update messages and add progress messages for getCoOccurrence (BMI and Alg).

## Changes in Version 0.1.0.9282 (2020-09-09)
* CASTool
    + server.R
        - Add message output for testing on shinyapps.io.

## Changes in Version 0.1.0.9281 (2020-09-09)
* CASTool
    + global.R
        - Reinstate "." and change SMCSitesFinal read line.

## Changes in Version 0.1.0.9280 (2020-09-09)
* CASTool
    + global.R
        - Modify file.path to not use "."

## Changes in Version 0.1.0.9279 (2020-09-09)
* Logos
    + Add hi-res logos to each Shiny app in www folder
    + Test logo in Shiny apps in ui.R
    + Remove raw-data hexSticker code and old logos.
* CASTool
    + server.R, run_ALL2
        - Load RDA rather than SHP files for mapping.  Saves ~ 25 seconds.
* getSiteInfo
    + Add extra condition for photo directory but no photo files.
* getReport
    + Fill in description for 2 parameters.

## Changes in Version 0.1.0.9278 (2020-09-08)
* getReport.R
    + Add SiteQual2Print as parameter.
    + Change dir_results default.
* CAST server.R
    + Add siteQual2Print as input for getReport.
* Rename CAST to CASTool
* Rename RPP to RPPTool

## Changes in Version 0.1.0.9277 (2020-09-02)
* Replace data file SMCSitesFinal.tab.
* Shiny RPP, server.R
    + TargetSiteID to TargetCOMID.
    + Split up user inputs.

## Changes in Version 0.1.0.9276 (2020-08-31)
* Update version numbers in NEWS, DESCRIPTION
    + In Shiny apps use date.

## Changes in Version 0.1.0.9275 (2020-08-31)
* Multiple changes in RPP Shiny app.
   + Added as pull request from 20200831 branch.
* Shiny CAST_SMC
    + Revised data.
    + Small tweaks
        - CASTool_CA.R
        - server.R
* Shiny CAST_SMC, server.R
    + Enable map zoom on station select.
* Update README.

## Changes in Version 0.1.0.9274 (2020-08-31)
* CASTool_CA.R
    + Change from file.path(wd, "Results"... to file.path(dir_results...

## Changes in Version 0.1.0.9273 (2020-08-28)
* getSiteInfo.R
    + Set boo_DEBUG <- FALSE
* getStressorList.R
    + Add na.rm=TRUE to geom_jitter to avoid warning about missing points.
* CASTool_CA.R
    + Modify skeleton code for debugging.

## Changes in Version 0.1.0.9272 (2020-08-28)
* Update NEWS with yesterday's changes.

## Changes in Version 0.1.0.9271 (2020-08-27)
* v0.1.0.9003 …
* Updated to reflect changes in dplyr::arrange()
* Commented out CASTfxn Package version until I can install it

## Changes in Version 0.1.0.9270 (2020-08-27)
* v0.1.0.9263 …
* Updates to address changes to dplyr::summarise() and dplyr::mutate(); 
    + changes to allow missing modified streams and 303d-list files; 
    + changes to use dir_results instead of wd, "Results" so there's only one location to specify the results directory and it doesn't have to be the working directory.

## Changes in Version 0.1.0.9269 (2020-08-27)
* v0.1.0.9261 …
* Changes to standardize debugging results directory; 
    + updates to account for changes in the new version of dplyr

## Changes in Version 0.1.0.9268 (2020-08-27)
* v0.1.0.9263 …
* Updated code to reflect changes in new dplyr version regarding summarise() and mutate()

## Changes in Version 0.1.0.9267 (2020-08-27)
* v0.1.0.9256 …
* Adjusted dplyr::summarise() to reflect new version of dplyr package; 
    + rewrote lines to identify whether or not the parameter should be log10 transformed

## Changes in Version 0.1.0.9266 (2020-08-27)
* v0.1.0.9247 …
* added any to vector comparison and adjusted dplyr::summarise() to reflect updates to the dplyr package

## Changes in Version 0.1.0.9265 (2020-08-27)
* v0.1.0.9263 …
* Revised to allow NULL for data_mods and data_303d; 
    + adjusted directories to reflect the directory variables as stated in the skeleton code ONLY in the debugging statement.

## Changes in Version 0.1.0.9264 (2020-08-27)
* v0.1.0.9246 …
* Updated dplyr::summarise()

## Changes in Version 0.1.0.9263 (2020-08-27)
* v0.1.0.9244 …
* updated dplyr::summarise()

## Changes in Version 0.1.0.9262 (2020-08-27)

* Post merge update.
* getSiteInfo.R
    + wd/"Results" to dir_results
    + Parameter AlgIndexGpGp to AlgIndexGp
    + df_bkginfo to data_bkginfo
* CAST_SMC Shiny
    + server.R (CAST_SMC)
        - Update Run_ALL to Run_ALL2 with skeleton code.
        - Compared code chunks via https://text-compare.com/
    + Update Help section.
* getWoE.R
    + Outlining.

## Changes in Pull Request #88.9001 (2020-08-21).

* CASTool_CA.r 
    + Move from R/ to inst/extdata/
    + Change gitpath from local PC to system.file
    + Comment out source for package functions.
    + wd to getwd()

## Changes in Version 0.1.0.9260 (2020-08-20)

* Shiny CAST_SMC
    + Add help file and make active.
        - Create RMD and create file in data-raw folder.
    + Make Map legend key file active.
    
## Changes in Version 0.1.0.9259 (2020-08-19)

* GGplots, add na.rm = TRUE for geom_* and *_smooth.  Issue #87
    + getBioStressorResponses.
    + getCoOccur
        - Formatting only.  Already included na.rm.
* Fixes from merge.
    + getSummaryAllSites.R
        - Reference to local directory included in merge.
    + getTimeSeq
        - Duplicate "stressors" parameter
* runShinyExamples.R
    + Update for current names of Shiny apps in package.
* getWoE.R
    + Parameters didn't match the function.
    
## Changes in Version 0.1.0.9258 (2020-08-17)

* Rebuild and repost.

## Changes in Version 0.1.0.9257 (2020-08-17)

* Merged 201909_ARL branch as pull request #86.

## Changes in Version 0.1.0.9256 (2020-08-17)

* Tweak to Shiny app CAST_SMC

## Changes in Version 0.1.0.9255 (2020-08-15)

* dplyr::summarize(), add .groups = "drop_last"
    + Shiny app CAST_SMC
    + Shiny app RPP_SMC

## Changes in Version 0.1.0.9254 (2020-08-14)

* Shiny
    + CAST_SMC
        - Fix map by disabling plot legend explanation.
    + Remove unused Shiny apps
        - CAST_Map_COMID
        - CAST_Map_StationID

## Changes in Version 0.1.0.9253 (2020-08-11)

* Shiny, RPP_SMC
    + Targeted SiteID and COMID to top of pick lists.
* Shiny, RPP_CAST
     + Targeted SiteID to top of pick lists.

## Changes in Version 0.1.0.9252 (2020-08-11)

* Vignettes
    + CASTfxn, not working
    + Slight tweaks to Analysis and Elevation.
* Shiny, RPP_SMC
    + Station map shows corresponding COMID for selected StationID.
* Shiny, RPP_CAST
    + Attempt to fix station map

## Changes in Version 0.1.0.9251 (2020-07-31)

* File clean up.
* Add version numbers to titles of Shiny apps (RPP_SMC and CAST_SMC).

## Changes in Version 0.1.0.9250 (2020-05-04)

* Shiny app, RPP_SMC
   + Rework visual design.
   + Include Stations map as a tab.
   + Include Reach map as a tab.
   + Other tweaks.

## Changes in Version 0.1.0.9249 (2020-04-23)

* Shiny app, RPP_SMC
    + Add user inputs.
    + Currate included data.

## Changes in Version 0.1.0.9248 (2020-04-20)

* Report_Results_summary.rmd
    + Replace CSCI and MMIdiatom with bmiIndex and algIndex.
    + arrange_ to arrange (line 271) to avoid deprecation message.
* getReport
    + Define pipe so can be used in RMD.
    + Additional input parameters
        - dir_data
        - bmiIndex
        - algIndex
    + Modify message for missing RMD.
    + Formatting to avoid error when render the RMD.
* CAST_SMC
    + server.R
        - Update call to getReport()
* getSummaryAllSites.R
    + print() to message()
    + Replace list.files() and checks for files with list.dirs().
    + Fix formatting on an if else statement.
* Shiny CAST_COMID
    + Stream reaches not showing, uncommented that section.

## Changes in Version 0.1.0.9247 (2020-04-15)

* Shiny map apps CAST_Map_StationID and CAST_MAP_COMID
    + Add mini map

## Changes in Version 0.1.0.9246 (2020-04-14)

* getSiteInfo.R
    + Clear warning about only first element used.
* getBioStressorResponses
    + Add "formula = y ~ x" to avoid message.

## Changes in Version 0.1.0.9245 (2020-04-13)

* getReport.R
    + Add "useBC" and "lagdays" as input parameters.
* getQualSites.R
    + Fix working directory reference.
* Shiny CAST_SMC
    + server.R, Run_ALL
        - Add "stringsAsFactors = FALSE" to read.delim().
    + dplyr::select
        - Add "all_of".  More tidyverse stuff.
* Report_Results_summary.rmd
    + Comment out lines without inputs.
        - siteQual2Plot
        - DOlim
        - pHlimLow
        - pHlimHigh
* SiteInfo.R
    + Modify is.na to avoid more tidyverse corruption.
        - is.na(df.temp$StudyYear)
        - is.na(df.temp[, "StudyYear", TRUE])
* getOutliers.R
    + Get rid of 'NaN' introduced warning.
        - Add filter for LogTranf == 1 and ResultValue <= 0.

## Changes in Version 0.1.0.9244 (2020-04-10)

* getVerifiedPredictions
    + Update with drop = TRUE to deal with tidyverse corruption of data formats.
* runShinyExamples.R
    + Update examples, details, and default (CAST_SMC).
* Shiny_SMC
    + Change order of tabs to have Console first.
    + Copy disclaimer to sidebar.
    + Rename Disclaimer_Key to Legend_Key.
        - Minor edits.

## Changes in Version 0.1.0.9243 (2020-04-09)

* 2020-04-09, found missing from GitHub.  Reloaded version from 2020-02-05.
* Updates to CAST_SMC shiny.
    + Code tweaks.
    + Test sites to top of SMCSitesFinal.tab
    + Suppress warning for readOGR.
    + Update Disclaimer to most recent version.
    + Update progress bar.
* Declare additional parameters and fix working directory references.
    + getSiteInfo
    + getQualSites
    + getClusterInfo
    + getTimeSeq
    + getBioStressorResponses
    + getVerifiedPredictions
    + getWoE
* Send print to message
    + getSiteInfo
    + getTimeSeq
    + getVerifiedPrecitions
    + getWoE
* ggplot add na.rm
    + getTimeSeq

## Changes in Version 0.1.0.9242 (2020-02-03)

* Update data in Shiny_SMC folder.
    + Data from collaborator's most recent version.

## Changes in Version 0.1.0.9241 (2020-01-30)

* Fixes to Shiny Apps
    + CAST_Map_StationID
        - Renamed from SiteID to StationID.
    + CAST_SMC
        - Partial fix.  Runs but not completely.

## Changes in Version 0.1.0.9240 (2020-01-27)

* Create new package after merging branches and resolving conflicts.

## Changes in Version 0.1.0.9239 (2019-10-07, ARL)
* General
    + Minor bug fixes arising from system test to various functions
* getSummaryAllSites
    + Summarizes WoE from all target sites in the results folder

## Changes in Version 0.1.0.9238 (2019-10-01, ARL)
* General
    + Standardized variable and column names to minimize confusion
* getStressorList
    + Adjusted for using only one cluster rathern than multiple options
    + Adjusted graphs to display quality type instead of "all ref" always
* getCoOccurDataSet
    + Generalized "CSCI" or "IBI" to be contents of variable "index"
* getBioStressorResponses
    + Adjusted graphs to display quality type instead of "all ref" always
    
## Changes in Version 0.1.0.9237 (2019-09-27, ARL)
* SMCClusterData.tab
    + Removed extraneous columns (clust_land, clust_noland, TempWS, PrecipWs)
* Map_Leaflet.rmd
    + Adjusted calls that relied on multiple cluster options to just one cluster
* getSiteInfo
    + Adjusted for using only one cluster rather than multiple options
* getClusterInfo
    + Adjusted for using only one cluster rather than multiple options
    + Adjusted graph to display quality type instead of "all ref" always
    + Adjusted graph title to be more descriptive
    + Added caption to better describe quality type


## Changes in Version 0.1.0.9236 (2019-9-26)

* getComparators, new function
    + Uses cluster identification as base comparator set
    + Adds BC dissimilarity distance matrix if useBC = TRUE
    + Identifies a minimum of 30 comparator sites from sites
    having <= bc.cutoff value dissimilarity; exceeds cutoff
    if <30 sites meet criteria; uses all sites meeting
    criteria, even if >30.

* getCoOccurDataset, new function
    + Identifies paired stressor/response data with a user-
    specified lag time (default = 0) and creates a data set.
    + This dataset is generated prior to selecting stressors
    for analysis as potential causes of impairment.
    + Biocomm-specific, but inclusive of measured/modeled data.
    + Part of the data prep part of the CASTool.

* getDataGaps, new function
    + Assembles data gaps identified by other functions into a single table.

* getDataSets, new function
    + Similar to getCoOccurDataset, but filtered for only stressors
    that will be used in further analyses to evaluate evidence for causality.

* getQualSites, new function
    + Identifies sites, reaches and samples representing reference
    conditions, as identified by the regulatory authority and
    specified in the Sites data file; sites considered to be
    not degraded, also as identified by the regulatory authority's
    numerical threshold for "degraded"; and sites having samples
    with "better" quality than the worst quality target site sample.

* getSiteBackground, new function
    + Identifies StreamCat data illustrative of anthropogenic activity
    that might be found to relate to causal agents. Although it makes
    no claims about these agents, barplots of their values are presented
    at multiple scales, if available.
    + Moves site files from a data folder repository into the target site 
    results folder.

* getTimeSeq, new function
    + Prepares barplots of stressor/response values over time, with each
    stressor/response pair graphed separately, one atop the other.

* getWoE, new function
    + Pulls together the weight of evidence findings from each separate
    line of evidence evaluated for the target site and biological community.
    
## Changes in Version 0.1.0.9235 (2019-9-05)

# # Changes in Version 0.1.0.9235.007 (2020-01-27)

* Disclaimer_Key

    + Move creation to data-raw
    
    + Move file location folder from data to www.
    
* NEWS - modify structure.

# Changes in Version 0.1.0.9235.006 (2019-11-06)

* Add package down website.
    + Partial.

# Changes in Version 0.1.0.9235.005 (2019-10-29)

* Shiny_SMC
    + Move Results back out of www folder.
    + Function to copy Results to www.
    + Add function to end of Run_All.
    + Remove www\Results in global.
    + ObserveEvent on StationID for CopyResults.

# Changes in Version 0.1.0.9235.004 (2019-10-28)

* Shiny_SMC
    + Move Results to www folder.
    + Add PDF viewer to each tab.

# Changes in Version 0.1.0.9235.003 (2019-10-28)

* Shiny, Disclaimer_Key.HTML
    + toc_depth from 3 to 2.
        - Takes up less space.

# Changes in Version 0.1.0.9235.002 (2019-10-28)

* Updates for state of files as of COB 10-24.

# Changes in Version 0.1.0.9235.001 (2019-10-28)

* New Branch on GitHub (201910_Shiny_SMC)
* Roll back to 2019-10-24 close of business edits.
* Keep branch code for Shiny app modifications while also have a branch for code edits.  Will merge later.

# Changes in Version 0.1.0.9235 (2019-09-05)

## Changes in Version 0.1.0.9236 (2019-10-22)

* Update Shiny app CAST_SMC.
    + Add data.
    + Modify to use SMC data.
* DESCRIPTION, packages under IMPORTS
    + Add
        - readxl
        - tidyr
        - shinyFiles
    + Remove
        - RgoogleMaps

## Changes in Version 0.1.0.9235 (2019-09-05)

* getStressorList, Issue #82
    + Add "DirIncStress" to chem.info (raw data).
    + Use new parameter to decide on how to deal with probsHi and probsLo.
    + Previously looked only for "DO" or "pH". 
* getCoOccur, Issue #82
    + Update example to use data.chem.info$DirIncStress to get col.Stressors.InvSc input.

# Changes in Version 0.1.0.9234 (2019-09-05)

* getStressorList, Issue #81
    + File save, remove row names (line 372).

## Changes in Version 0.1.0.9233 (2019-09-05)

* getCoOccur
    + Modify "pH" in defaults for col.Stressor.InvSc.

# Changes in Version 0.1.0.9232 (2019-07-11)

* Shiny, map
    + Update map data for SMC.

# Changes in Version 0.1.0.9231 (2019-07-11)

* Shiny, map, 2 versions, COMID and SiteID

# Changes in Version 0.1.0.9230 (2019-06-26)

* Working on Shiny app.  Incomplete.  Issue #30.
    + Renamed CAST_v3 to CAST_AZ
    + Nearly complete.
    + Removed CAST_v1 and CAST_v2.
* getClusterInfo
    + Tweaks for Shiny App
    + Formatting.
    + boo_DEBUG for testings.

# Changes in Version 0.1.0.9229 (2019-06-24)

* getClusterInfo, Issue #76
    + Add data.cluster as input parameter.

# Changes in Version 0.1.0.9229 (2019-06-24)

* getClusterInfo, Issue #80
    + Add TargetSiteID as input parameter.

# Changes in Version 0.1.0.9228 (2019-06-24)

* getBioStressorResponses, Issue #79
    + Suppress warnings for "predict".

# Changes in Version 0.1.0.9227 (2019-06-24)

* Working on Shiny app.  Incomplete.  Issue #30.
* getSiteInfo, Issue #78
    + Update code to use function variable map_proj instead of example variable my.aea.

# Changes in Version 0.1.0.9226 (2019-06-06)

* getBioStressorResponses, Issue #75
    + Modify lm() sections.
        - Convert NAN/Inf to NA
        - na.action inside of lm()

# Changes in Version 0.1.0.9225 (2019-06-06)

* Update ShinyApp included in package, Issue #30
    + runShinyExample
        - Use CAST_v3
    + Add shinyjs to DESCRIPTION Imports
    + Still working
* Update console feedback to messages, Issue #73
    + So can trap in Shiny app and display to user.
    + getCluster.R
    + getBioStressorResponses
* Add output directory to Return section of help file.
    * getSiteInfo
    * getClusterInfo
    * getCoOccur
    * getVerifiedPredictions

# Changes in Version 0.1.0.9224 (2019-05-31)

* Add testing, Issue #72.

# Changes in Version 0.1.0.9223 (2019-05-31)

* runShinyExample, Issue 30
   + Added additional Shiny Apps to the package.
       - CAST_MapSelection, was already in the package
       - CAST_v1, original design
       - CAST_v2, for testing of new app
   + Added parameter to function to run the different Shiny apps.

# Changes in Version 0.1.0.9222 (2019-05-20)

* getCoOccur
    + Modify scoring on box plot for DO and pH, Issue #70
    + Add new input variable for those with inverse scoring.
        - Use 25/50 instead of 50/75 as scoring threshold quantiles.
        - Scores are 1/0/-1 instead of -1/0/1
    + Modify scoring threshold quantiles on box plot.

# Changes in Version 0.1.0.9221 (2019-05-20)

* getCoOccur
    + Modify scores for SR plot (plot2), Issue #71
    + Scores are in ascending order so Stressor Response plot matches Box plot.
    + Scores file output is now ordered by Param_Value instead of IBI.
* DESCRIPTION
    + Removed "StagedInstall: yes"

# Changes in Version 0.1.0.9220 (2019-05-16)

* Changes for R 3.6.0 devtools, Issue #65
    + Readme
        - Rebuild.

# Changes in Version 0.1.0.9219 (2019-05-16)

* Changes for R 3.6.0 devtools, Issue #65
    + Readme
        - Fix misspelling in installation example.

## Changes in Version 0.1.0.9218 (2019-05-16)

* Changes for R 3.6.0 devtools, Issue #65
    + Readme
        - Moved install code inside of code box.
        - Added "help" section.
        - Updated badges, https://github.com/Naereen/badges

# Changes in Version 0.1.0.9217 (2019-05-16)

* Changes for R 3.6.0 devtools, Issue #65
    + Need extra line for install from GitHub.  Update readme.
        - Sys.setenv("TAR" = "internal")
* GitHub badges
    + Added Maintained to Readme.
    + https://github.com/Naereen/badges

# Changes in Version 0.1.0.9216 (2019-05-16)

* Changes for R 3.6.0 staged install, Issue #65
    + Do not store package directory to any object.  Always call with system.file.
        - getReport.R
        - getSiteInfo.R
* DESCRIPTION, Issue #69
    + Update for package changes that are no longer used in CASTfxn.
        - replyr, remove from Imports, package in maintenance mode
        - pryr, removed from Suggests, used prior to conversion to all ggplot2 plots.

# Changes in Version 0.1.0.9215 (2019-05-16)

* getBioStressorResponse
    + Modify correlation file output, Issue #68
        - Update QC check for new "n" column.

# Changes in Version 0.1.0.9214 (2019-05-15)

* getVerifiedPredictions
    + Add biocomm as input.
        - help file
        - example
        - function code
    + Score file modifications, Issue #68
        - Add "n".
        - Rename (include biocomm)
* getBioStressorResponse
    + Score file modifications, Issue #68
        - Correlations file, add "n".

# Changes in Version 0.1.0.9213 (2019-05-14)

* getVerifiedPredictions
    + Update description Value.

# Changes in Version 0.1.0.9212 (2019-05-13)

* getVerifiedPredictions, Issue #57
    + Add "n" to plot in caption.
    + Add scoring boundaries.
    + Add scores to the plot caption.
        - In ascending order to match plot (left to right).
    + Modify scores output file.  Issue #61
    + Error/stop message for no "worse" bio sites for comparison.

# Changes in Version 0.1.0.9211 (2019-05-10)

* getVerifiedPredictions, Issue #57
    + Add better bio, degraded = no points to the plot

# Changes in Version 0.1.0.9210 (2019-05-09)

* getReport fails, Issue #67
    + Update for changes in BioStressorResponses scores output, Issue #58

# Changes in Version 0.1.0.9209 (2019-05-06)

* Fixes after running "check" in RStudio.
    + Add package reference to functions that are not base package functions.
        - importFrom("grDevices", "pdf")
        - importFrom("graphics", "plot")
        - importFrom("stats", "lm", "predict", "var")
        - importFrom("utils", "flush.console", "read.delim")
    + examples lines wider than 100 characters
        - getBioMatches
        - getBioStressorResponses
        - getChemDataSubsets
        - getClusterInfo
        - getSSDplot
        - getSiteInfo
        - getStressorList
        - getVerifiedPredictions
    + Document data
        - data_CoOccur_AZ_Lo
* R v3.6.0., StagedInstall, Issue #65
    + DESCRIPTION
        - StagedInstall: yes

# Changes in Version 0.1.0.9208 (2019-05-06)

* getBioStressorResponse, Issue #58.
    + 2nd Score.
    + Add scores to plot.
    + Rework output table.
* Add SiteID to all text file outputs, Issue #66
    + getBioStressorResponse
        - SRCKN001.61.SR.BMI.Scores.txt

# Changes in Version 0.1.0.9207 (2019-05-02)

* getSSDplot
    + Add na.rm=TRUE to ggplot references to avoid warning messages, Issue #56.

# Changes in Version 0.1.0.9206 (2019-05-02)

* R v3.6.0., StagedInstall, Issue #65
    + DESCRIPTION
        - StagedInstall: no
    + Use system.file(package="") without saving to a variable.
        - runShinyExample.R
        - getReport.R
        - getSiteInfo.R
* getSiteInfo
    + Update leaflet map RMD with SiteInfo subdirectory for static map.  Issue #64

# Changes in Version 0.1.0.9205 (2019-05-01)

* Shiny App, Issue #30.
    + Add COMID select with map.
* Sub-directories by function, Issue #64
    + Report and most functions.

# Changes in Version 0.1.0.9204 (2019-04-26)

* getBioStressorResponses
    + Tweaks trying to find why fails for a user.
        - Formatting in code.
        - Algae example.
        - QC check on cor file header add "biocomm". 

# Changes in Version 0.1.0.9203 (2019-04-25)

* biocomm name on file scoring outputs, Issue #64.
    + getBioStressorResponses.
        - Add to table outputs.
    + getCoOccur
        - Add as input.
        - Add to txt output filenames.
        - Add to table outputs.
    + getStressorList
        - Add as input.
        - Add to txt output filenames.
        - Did **not** add to table outputs.
    + getReport
        - Modify RMD for new file names.
        - Add DT for tables.
* Add DT package to DESCRIPTION IMPORTS.

# Changes in Version 0.1.0.9202 (2019-04-25)

* Remove function getRegPlotSet, Issue #63.

# Changes in Version 0.1.0.9201 (2019-04-23)

* Remove unused inputs, Issue #60
    + getVerifiedPredictions
        - predint
        - varLegLoc
    + getBioStressorResponses
        - predint
        - varLegLoc

# Changes in Version 0.1.0.9200 (2019-04-23)

* getVerifiedPredictions
    + Make inputs more generic, Issue #59
        - "bmi" to "bio".

# Changes in Version 0.1.0.9199 (2019-04-23)

* getCoOccur
    + Example 2 (AZ) site to SRCKN001.61 to match other examples.

# Changes in Version 0.1.0.9198 (2019-04-23)

* getBioStressorResponses
    + Scoring.  No slope score to zero.

# Changes in Version 0.1.0.9197 (2019-04-23)

* Declare "directory" as a required input.
    + getStressorList
    + getBioStressorResponses
    + getVerifiedPredictions
    + getClusterInfo
* getVerifiedPredictions
    + Rename function.
        - Earlier update only did file name.
* getBioMatches
    + Update names in output.

# Changes in Version 0.1.0.9196 (2019-04-22)

* getBioMatches
    + Missing inputs:
        - data.stress.raw
        - data.bioMetrics
        - list.SiteSummary
        - data.SampSummary
        - data.chem.raw
    + Update documentation.
    + Update examples.
    + Update code; bio instead of bmi and alg.
* Update examples for changes to getBioMatches
    + CASTfxn_Vignette.RMD

# Changes in Version 0.1.0.9195 (2019-04-22)

* Rename getStressorSpecificRegressions to getVerifiedPredictions
    + getStressorSpecificRegressions.R
    + CASTfxn_Vignette.RMD
    + Analysis.RMD
* CASTfxn_Vignette.RMD
    + Update examples for updates in functions.

# Changes in Version 0.1.0.9194 (2019-04-22)

* Remove old deprecated functions.

# Changes in Version 0.1.0.9193 (2019-04-18)

* getBioStressorResponses
    + Set minimum number of cluster samples 3 rather than 1.
        - predict and corr.test were failing with only 2 records.

# Changes in Version 0.1.0.9192 (2019-04-18)

* getCoOccur
   + Allow for special characters (e.g., %) in stressors.
   + Error message for stressors not in input data.

# Changes in Version 0.1.0.9191 (2019-04-17)

* getCoOccur
    + Attempt to remove warning messages from plot 1 (p1).
        - If skip geom_jitter the plot is missing parts so leave alone.

# Changes in Version 0.1.0.9190 (2019-04-17)

* getBioStressorResponses
    + Update regression plot with 2nd regression line.  Issue #55.

# Changes in Version 0.1.0.9189 (2019-04-16)

* getCoOccur
    + Unwind removing Stressor plot.  Keep for now. Issue #54.
    + Make edits to p2 to avoid warnings; Issue #56.

# Changes in Version 0.1.0.9188 (2019-04-16)

* Add na.rm=TRUE to ggplot statements to avoid warnings; Issue #56.
    + getCoOccur

# Changes in Version 0.1.0.9187 (2019-04-16)

* getCoOccur
    + Remove stressor plot (p2).  Issue #54

# Changes in Version 0.1.0.9186 (2019-04-15)

* getBioStressorResponses
    + Fix 'df.corr' object not found.
        - Previously renamed df.corr to df.corr_cl.  Missed a reference.

# Changes in Version 0.1.0.9185 (2019-04-15)

* getCoOccur
    + NA for stressor values.
        - Parameter was being skipped if no stressor values (i.e., all NA).
        - Output NA to scores file.
        - Message to console.

# Changes in Version 0.1.0.9184 (2019-04-12)

* getBioStressorResponses
    + Minor edits to 0.1.0.9083 changes (r2).
    + Check for missing stressors.
        - Remove from stressor list.
        - Warning for those requested but missing from data.

# Changes in Version 0.1.0.9183 (2019-04-12)

* getBioStressorResponses
    + Modify linear regression plot, Issue #55.
    + Incomplete.  Still need 2nd regression for just the cluster.

# Changes in Version 0.1.0.9182 (2019-04-12)

* Move the SR plot from getCoOccur to getBioStressorResponses, Issue #54.
    + Prepare code, did not make changes.

# Changes in Version 0.1.0.9181 (2019-04-12)

* getBioStressorResponses
    + Update stop message for no response data.

# Changes in Version 0.1.0.9180 (2019-04-12)

* make.names; undo edits for TargetSiteID in names for folders and files.
    + Some start with numbers and that is ok.
    + getBioStressorResponses
    + getClusterInfo 
    + getCoOccur
    + getStressorList
    + getStressorSpecificRegressions
* getCoOccur
    + Boxplot not saving to TargetSiteID folder (line 414).

# Changes in Version 0.1.0.9179 (2019-04-11)

* getBioStressorResponses
    + Line 262-267 QC check failed.
        - Move declaration into previous if/then by biocomm.
* Use make.names for ggsave exports of plots by variable.
    + getBioStressorResponses
    + getStressorSpecificRegressions
    + getCoOccur
    + getClusterInfo

# Changes in Version 0.1.0.9178 (2019-03-22)

* getBioStressorResponses
    + End if no site response data (list.MatchBioData$site.a.rsp).

# Changes in Version 0.1.0.9177 (2019-03-22)

* getCoOccur
    + End message for no data rather than error crash.
    + ID.plot to TargetSiteID
        - For consistency among functions.
    + dir.plots parameter not being used.  Modify code to use it.
    + Example, remove "c" from col.ID.

# Changes in Version 0.1.0.9176 (2019-03-21)

* Report_Results_summary
    + lines 155-175, SR.BMI.Scores.  read statement corrected.

# Changes in Version 0.1.0.9175 (2019-03-21)

* Report_Results_summary
    + lines 132-152, SR.BMI.Corrs.  read statement corrected.

# Changes in Version 0.1.0.9174 (2019-03-15)

* Report_Results_summary
    + Update show CoOccur for uneven box and SR plots.

# Changes in Version 0.1.0.9173 (2019-03-15)

* Report_Results_summary
    + Show SSTV plots.
    + Update show CoOccur for no data.

# Changes in Version 0.1.0.9172 (2019-03-15)

* Report_Results_summary
    + Show CoOccurrence plots.

# Changes in Version 0.1.0.9171 (2019-03-13)

* getBioStressorResponses
    + Modify QC check for header for correlation plot data.
       - Resave file.
* Report_Results_summary
    + Make same modification as getBioStressorResponses.

# Changes in Version 0.1.0.9171 (2019-03-13)

* getBioStressorResponses
   + Add QC check for header for correlation plot data.

# Changes in Version 0.1.0.9170 (2019-03-11)

* getStressorSpecificRegressions
    + Add ref.sites as a required input parameter.
* Add na.rm=TRUE to fun.aggregate=mean for dcast statements.
    + getBioStressorResponses.R
    + Report_Results_summary.rmd

# Changes in Version 0.1.0.9169 (2019-03-11)

* Assign cluster in "algae" example.
* getBioStressorResponses
    + Update scores text file output for header row.
        - If case 1 didn't have results the file didn't have a header row.
        - And the report would fail.
* getReport
    + Report_Results_summary.rmd
        - Update dcast statement to include fun.aggregate = mean.

# Changes in Version 0.1.0.9168 (2019-03-08)

* Modify QC procedures for plotting missing categories of data.
    + getStressorRef
    + getClusterInfo  
    + getBioMatches   
    + getBioStressorResponses 

# Changes in Version 0.1.0.9167 (2019-03-08)

* Assign data.cluster based on information in data_Sites.
    + Modify examples in each function.
        - getSiteInfo
        - getChemDataSubsets
        - getBioMatches
        - getBioStressorResponses
        - getClusterInfo
        - getStressorList
        - getStressorSpecificRegressions

# Changes in Version 0.1.0.9166 (2019-03-07)

* getBioStressorResponses
    + Fix errors from testing.
        - Remove extra brackets for sections.
        - Add extra QC on correlation plot.
        - Output item message for ones skipped.

# Changes in Version 0.1.0.9165 (2019-03-05)

* getStressorList
    + Fails when have no reference sites.
        - Change trigger for plotting ref sites.

# Changes in Version 0.1.0.9164 (2019-03-05)

* getStressorSpecificRegressions.R
    + Revised plot output.  Issue #50 and 44.
    + Old function R file renamed (prefixed with "z_") and marked with keyword "internal".
    + Remove stressor loop.  Always sens and tol taxa.
* Data
    + Rebuild all data from raw data files using processing scripts.
    + Use dataset received 2019-02-27.
* getSSDplot
    + Update example to 'print' plots.
* getCoOccur
    + cluster to comparator.
        - Variables in function only.
* getBioStressorResponses
    + Ensure Alg version works, Issue #46
    + Update example to remove bad response variables, Issue #46
* DESCRIPTION
    + Move pryr package from imports to suggests.  Issue #52.

# Changes in Version 0.1.0.9163 (2019-02-26)

* getClusterInfo.R
    + Fix y-axis label the same for all plots, Issue #48.

# Changes in Version 0.1.0.9162 (2019-02-19)

* getStressorSpecificRegressions.
    + ggplot graphics, Issue #41.
    + Started but unfinished.
    + Other changes proposed to this function.

# Changes in Version 0.1.0.9161 (2019-02-18)

* Add geom_blank for ggplots where may not have a data group (e.g., cluster ref).  
* Use same structure as in getBioStressorResponses.
    + getStressorList
    + getClusterInfo

# Changes in Version 0.1.0.9160 (2019-02-15)

* getStressorList 
    + Change "box" plots to ggplot.  Issue #41.
    + Remove importFrom pryr "%<a-%". 

# Changes in Version 0.1.0.9159 (2019-02-15)

* getRegPlotSet 
    + Mark functions as keyword internal so not in the help list

# Changes in Version 0.1.0.9158 (2019-02-15)

* getBioStressorResponses
    + Remove importFrom pryr "%<a-%".
        - No longer needed with gglot graphics.

# Changes in Version 0.1.0.9157 (2019-02-15)

* getClusterInfo
    + Updated plot title to match old graphic.  Issue #41.

# Changes in Version 0.1.0.9156 (2019-02-14)

* getClusterInfo
    + Convert to ggplot.  Issue #41.

# Changes in Version 0.1.0.9155 (2019-02-14)

* getBioStressorResponse
    + Fix plot error when missing a subset of data.  Issue #43.

# Changes in Version 0.1.0.9154 (2019-02-11)

* getBioStressorResponse
    + Fix PDF output after conversion to ggplot.

# Changes in Version 0.1.0.9153 (2019-02-08)

* getBioStressorResponse
    + Add ref.sites as an input.
    + Update to ggplot, Issue #7
    + Edit code for clarity

# Changes in Version 0.1.0.9152 (2019-02-07)

* getClusterInfo
    + Fixed siteClusters v. site.Clusters as a parameter.

# Changes in Version 0.1.0.9151 (2019-02-07)

* getBioStressorResponses, Issue #7
    + Convert plot to ggplot
        - Test mode so not active.

# Changes in Version 0.1.0.9150 (2019-02-06)

* getSiteInfo, Issue #32 and Issue #4
    + Add required objects to function input arguments.
    + Update example code
        - getBioMatches
        - getBioStressorResponses
        - getChemDataSubsets
        - getClusterInfo
        - getSiteInfo
        - getStressorList
        - getStressorSpecificRegressions 
    + Remove required columns in data.cluster input.  Issue #32.
        - W___AGRIC
        - W___URBAN
        - W___FOREST
    + leaflet map, Issue #42
        - Change addProviderTiles
        - Rename file and move inside Station folder.
    + ggplot map, Issue #14
        - Started but did not finish. 
        - Left code in as comments.
        - Map takes 10 to 15 seconds with ggplot.

# Changes in Version 0.1.0.9149 (2019-02-06)

* getStressorList
    + Error with NA reporting.  Issue #38.
        - Added extra is.na in getChemDataSubsets.
* getChemDataSubsets
    + Fix error with NA reporting.  Issue #38
    + Add in required parameters.  Issue #4
* Update examples
    + getBioMatches
    + getBioStressorResponses
    + getChemDataSubsets
    + getClusterInfo
    + getStressorList
    + getStressorSpecificRegressions

# Changes in Version 0.1.0.9148 (2019-02-05)

* Merget getBMIStressorRespones and getAlgStressorResponses into a single function, Issue #34
    + getBioStressorResponses
    + Deprecated BMI and Alg version with keyword internal.

# Changes in Version 0.1.0.9147 (2019-02-05)

* Merge getBMIMatches and getAlgMatches into single function, Issue #33.
    + getBioMatches 
    + Deprecated BMI and Alg version with keyword internal.

# Changes in Version 0.1.0.9146 (2019-02-04)

* Remove clustertype, Issue #31
    + Function inputs.
        - getSiteInfo
        - getClugerInfo
        - getChemDataSubsets
    + Function examples.
        - getAlgmatches
        - getAlgStressorResponses
        - getBMImatches
        - getBMIStressorResponses
        - getChemDataSubsets
        - getClusterInfo
        - getSiteInfo
        - getSTressorList
        - getStressorSpecificRegressions
    + Vignettes
        - CASTfxn_Vignette
        - Analysis
        
# Changes in Version 0.1.0.9145 (2019-02-04)

* Remove useLU, Issue #31
    + Function inputs.
        - getSiteInfo
        - getChemDataSubsets
        - getClusterInfo
        - getStressorList
    + Function examples.
        - getAlgmatches
        - getAlgStressorResponses
        - getBMIMatches
        - getMBIStressorResponses
        - getChemDataSubsets
        - getClusterInfo
        - getSiteInfo
        - getStressorList
        - getStressoSpecificRegressions
    + Vignettes
        - CASTfxn_Vignette
        - Analysis
    
# Changes in Version 0.1.0.9144 (2019-02-01)

* Add shiny to DESCRIPTION

# Changes in Version 0.1.0.9143 (2019-02-01)

* Add Shiny.  Issue #30.
    + Added demo app (default, not CAST).
    + Added runShinyExample function to launch Shiny.
        - Includes links in help file to Shiny.io app online.

# Changes in Version 0.1.0.9142 (2019-02-01)

* getCoOccur.R, Issue #25
    + Add individual plots as jpg.  
        - Use ggsave instead of jpeg (as with other functions).

# Changes in Version 0.1.0.9141 (2019-01-31)

* getCoOccur.R, Issue #25
    + Details
        - Use lowest biological condition score in box plots.
        - **Bold** section headers in details.
        - Changes to output (see below).
    + logistic regression
        - Ensure using Degraded Yes/No instead of Degraded/Reference.
    + Output
        - Save individuals JPG files as well as PDF.
    + Example
        - Modify example to be "Example 1, CA".
        - Add "Example 2, AZ hi".
    + Remove date from file names.
    + Use loweest biological score for a site.
        - Was mean.
    + Box plot.
        - Add scoring lines (as in SR plot).
        - Update text (make multiline).
    + Stressor Response (SR) Curve plot
        - Generate scores.
        - Save scores.
        - Add scores to plot.
* data
    + Modify data_CoOccur to be data_CoOccur_CA
    + Add data_CoOccur_AZ_Hi

# Changes in Version 0.1.0.9140 (2019-01-24)

* getCoOccur.R, Issue #25
    + Add debugging.
    + Rework factor of Bio.Deg to ensure always in the same order.
    + Box plot
        - Remove y-axis elements (was confusing).
        - Remove x-axis quotes around parameter name.
        - Modify shape and color of jitter points for use in legend.
        - Update legend.
        - Update y-axis so scaling matches Curve plot when combined in output.
    + Curve plot
        - Update points and legend to match box plot.

# Changes in Version 0.1.0.9139 (2019-01-18)

* Overall Report
    + getReport.R
    + inst/rmd/Report_Results_overall.rmd

# Changes in Version 0.1.0.9138 (2019-01-17)

* getReport
    + Modified QC check for "summary" report.
* Report_Results_summary.rmd
    + Minor tweaks.
    + BMI.SR plots show all with p value < 0.05.

# Changes in Version 0.1.0.9137 (2019-01-11)

* Update logtransf, Issue #23
    + getStressorSpecificResponses
        - Slightly different code.  Use example from getStressorList.

# Changes in Version 0.1.0.9136 (2019-01-10)

* Update logtransf, Issue #23
    + getAlgStressorResponses
    + getBMIStressorResponses

# Changes in Version 0.1.0.9135 (2019-01-10)

* getStressorList
    + Add LogTransf to output.  Issue #23

# Changes in Version 0.1.0.9134 (2019-01-10)

* Misnumbered v0.1.0.9033 as 9032

# Changes in Version 0.1.0.9133 (2019-01-10)

* getBMIStressorResponses
    + Ensure certain variables are not log transformed.  Issue #24.
        - DO, pH, temperature, flow
    + Tweak plot output from changes made in previous update.  Issue #23

# Changes in Version 0.1.0.9132 (2019-01-10)

* getBMIStressorResponses
    + Fix duplicate output to console.  Issue #23.

# Changes in Version 0.1.0.9131 (2019-01-07)

* getSiteInfo
    + Map_Leaflet.rmd missing
    + inst/RMD was mistakenly in .gitignore

# Changes in Version 0.1.0.9130 (2018-12-18)

* getSiteInfo
    + Add a leaflet map output as HTML (R Notebook).

# Changes in Version 0.1.0.9129 (2018-12-18)

* getAlgStressorResponses
    + Add PDF of plots.

# Changes in Version 0.1.0.9128 (2018-12-18)

* Update getReport template RMD for Algae corrplot.
    + \inst\rmd\Report_Results_summary.rmd

# Changes in Version 0.1.0.9127 (2018-12-18)

* Update data documentation
    + data_AlgCounts
    + data_AlgMasterTaxa
    + data_AlgMetrics
* getAlgStressorResponses
* data_AlgMetrics
    + Alg.Metrics.SampID to Algae.Metrics.SampID

# Changes in Version 0.1.0.9126 (2018-12-14)

* getAlgStressorResponses
    + Update with changes made to getBMIStressorResponses
* Update Algae Data
    + data_AlgMetrics
    + data_AlgMasterTaxa
    + data_Algcounts

# Changes in Version 0.1.0.9125 (2018-12-14)

* Vignette Update
    + CASTfxn
        - Change name shown in help file.
    + Add vignette for "anlaysis".
        - Run all functions example.
* Correlation output file column names.
    + getBMIStressorResponses.R
    + getStressorSpecificRegressions.R
    + getAlgStressorResponses.R

# Changes in Version 0.1.0.9124 (2018-12-13)

* getSSDplot
    + Add example to save created plot.
* getReport
    + Tweak summary report for names change of SSTV correlations file.

# Changes in Version 0.1.0.9123 (2018-12-12)

* getStressorSpecificRegressions
    + Modify inputs.
    + Add master taxa list.
    + Replace SampleID with BMI.Metrics.SampID
    + Limit data with unique so only get one instance.
    + Add user feedback for progress.
* Add master taxa data file.
    + Process raw data.
    + Data description.

# Changes in Version 0.1.0.9122 (2018-12-11)

* getBMIStressors
    + Update input variables.
    + Rename text output files to match other function outputs.
* Report_Results_summary.rmd
    + Update for change in text file outputs from getBMIStressors.

# Changes in Version 0.1.0.9121 (2018-12-10)

* getBMIStressors
    + Fix error in df.CorrTable creation.

# Changes in Version 0.1.0.9120 (2018-12-06)

* Modify plots to output a combined PDF as well as individual JPG files.  Issue #19.
    + .SSTV.
        - getStressorSpecificRegressions
* getStressorSpecificRegressions
    + Change data.chem.info2 to data.chem.info.
    + Add required objects as function inputs.
* Fix duplicated first line in txt output for stressor responses. Issue #17
    + getBMIStressorResponses
    + getStressorSpecificRegressions
    + getAlgStressorResponses

# Changes in Version 0.1.0.9119 (2018-12-06)

* Modify plots to output a combined PDF as well as individual JPG files.  Issue #19.
    + .SR.BMI.
        - getBMIStressorResponse

# Changes in Version 0.1.0.9119 (2018-12-06)

* Modify plots to output a combined PDF as well as individual JPG files.  Issue #19.
    + .cluster.
        - getClusterInfo
    + .SR.BMI.
        - getBMIStressorResponse
    + .SR.Alg.
        - getAlgStressorResponse
    + .SSTV.
        - getStressorSpecificRegressions
        
# Changes in Version 0.1.0.9118 (2018-12-06)

* Modify plots to output a combined PDF as well as individual JPG files.  Issue #19.
    + .boxes. 
        - getStressorList
* Added pryr package to aid in capture of plots for use in PDF output.

# Changes in Version 0.1.0.9117 (2018-12-05)

* Report
    + Add CoOccurrence table.
    + Add ChemPctRank table.
    + Only "summary" report.
        - Stop message for "all" report.

# Changes in Version 0.1.0.9116 (2018-12-05)

* getReport
    + Modify summary report to check if file exists
* getCoOccur
    + Modify user feedback to include overall item number; Issue #18
    + Modify file outputs to use "dot" delimiter to match other file outputs in package.
    + TSV to TXT for scores to match other data file outputs.

# Changes in Version 0.1.0.9115 (2018-11-13)

* getReport
    + Function to output report.
    + All and Summary reports.
       - Report_Results.RMD to Report_Results_All.RMD
       - Add Report_Results_Summary.RMD
* DESCRIPTION
    + Add rmarkdown to IMPORTS

# Changes in Version 0.1.0.9114 (2018-11-12)

* getBMIStressorResponses
    + Update jpg file name output.  Issue #16.
        - Missing "dot" between SiteID and BMI.SR.

# Changes in Version 0.1.0.9113 (2018-11-12)

* Report_Results.rmd
    + New results report.

# Changes in Version 0.1.0.9112 (2018-10-17)

* data.R
    + Remove non-ASCII characters so the package will build properly.
    + Chemical names and units combinations were the culprit; n=334.

# Changes in Version 0.1.0.9111 (2018-10-17)

* Elevation Vignette.

# Changes in Version 0.1.0.9110 (2018-10-16)

* data.R
    + data_SSD_generator, correct typo.  Issue #11.
    + Add more details to other data sets.

# Changes in Version 0.1.0.9109 (2018-10-16)

* Add getElev function.

# Changes in Version 0.1.0.9108 (2018-10-10)

* Vignette.
    + Fix errors.
* DESCRIPTION
    + Change R Depends from 2.1.0 to 2.10
    + Add Imports for sp and stringr
* Add utils:: for missing cases:
    + flush.console
    + write.table
* Non-standard names
    + getStressorList
        - boxes.water quality.x.jpg
        - Use make.names when build file names.
        - Don't need to adjust data.
    + Occurs in raw data; AZChemInfoFinal.tab
        - Category

# Changes in Version 0.1.0.9107 (2018-10-10)

* getSiteInfo
    + Add user defined "Results" folder.  Issue #13
    + Check for it and if not present create it.
    + Makes the function more generic.  Issue #4

# Changes in Version 0.1.0.9106 (2018-10-10)

* Merged Vignette branch (v0.1.0.9104) in previous committ (0.1.0.9105).
* Added project to TravisCI.
* ReadMe
    + Add badges.

# Changes in Version 0.1.0.9104 (2018-08-02)

* getCoOccur
    + Update save directory code.

# Changes in Version 0.1.0.9103 (2018-08-02)

* DESCRIPTION
    + Add authors in plain text
* CASTfxn.R
    + Revise with names of functions.
* Vignette
    + Add output descriptions.
* getStressorList
    + Add dot to filename of output after SiteID
    + SiteID.chem.pctrank.txt 
* getClusterInfo
    + Added ".cluster." after SiteID to output plot names.

# Changes in Version 0.1.0.9102 (2018-07-11)

* getBMIStressorResponses
    + More detailed console message.
* getStressorSpecificRegressions.
    + Modify QC check for horizontal and vertical lines.
    + Fix error with inset value for legend by using as.numeric.

# Changes in Version 0.1.0.9101 (2018-07-10)

* getClusterInfo
    + Add QC print output to code.
    + Added QC check to ensure Y data for box plot is not all NA or is not non-numeric.

# Changes in Version 0.1.0.9100 (2018-07-10)

* Use Ann's fork of CASTfxn as basis for fork in my repository.
* Jumping ahead to version "9100" to differentiate.
* Update NEWS
* getBMImatches 
    + lines 85:86
    + Missing closing paren for print.
* getclusterInfo
    + lines 95:96
    + Missing a comma in paste.
* getStressorSpecificRegressions
    + lines 128:129
    + Missing closing paren for print.


* TargetSiteID
    + Used in functions but is not a parameter.  
    + Assumed in the global environment.
    + QC checks fail.
    + Parameter in function call, example, and stop message if doesn't exist.
    + Add to the following functions:
    + getBMImatches (lines 85:86) [really just missing a parenthesis]
    + getClusterInfo (lines 95:96)
* Will need to follow up with examples in other functions.
    
# Changes in Version 0.1.0.9044 (2017-06-22)

* Add dataset "data_Cluster_Lo".
    + Add to data-raw and to data.R
* Add "ElevCategory" (HI or LO) to each data file in data-raw.
    + data_303d
    + data_AlgMetrics
    + data_BMIMetrics
    + data_BMIRelAbund
    + data_BMIcounts
    + data_Chem
    + data_Cluster_Hi
    + data_Cluster_Lo
    + data_ReachMod
    + data_SampSummary
    + data_Sites
* Files not modified:
    + data_ChemInfo
    + data_CoOccur
    + data_GIS_Flow_HI
    + data_GIS_Flow_LO
    + data_GIS_AZ_Outline
    + data_SSD
    + data_SSD_generator
    + data_SSD_permethrin

# Changes in Version 0.1.0.9043 (2017-06-21)

* getBMIStressorResponses
    + Review for scoring.
    + Change loop variable from r to q to avoid conflict with r and r2.

# Changes in Version 0.1.0.9042 (2017-06-21)

* getCoOccur
    + Fix help file with too wide text.

# Changes in Version 0.1.0.9041 (2017-06-21)

* getSSDplot examples.
    + Assign return plots to variables.
    + Additional example to demonstrate adding points to the plot.

# Changes in Version 0.1.0.9040 (2017-06-21)

* Scoring output.
    + getCoOccur

# Changes in Version 0.1.0.9039 (2017-06-20)

* Rename 2 functions with "get" to match others.
    + CoOccur
    + SSD
    + Update vignette.

# Changes in Version 0.1.0.9038 (2017-06-20)

* Update examples.  Issue #5.
    + getStressorSpecificRegressions
    + Use BMIRelAbund.rda for data.SSTV.totabund
    + Replace BenSampID with BMI.Metrics.SampID
    + Not finished.  Not working.
* Add data file; BMIRelAbund.rda
    + Include in data-raw and Data.R
    + Data for data.SSTV.totabund in getStressorSpecificRegressions.

# Changes in Version 0.1.0.9037 (2017-06-16)

* Update examples.  Issue #5.
    + getAlgStressorReponses
    
# Changes in Version 0.1.0.9036 (2017-06-16)

* Update examples.  Issue #5.
    + getAlgMatches

# Changes in Version 0.1.0.9035 (2017-06-16)

* Update examples.  Issue #5.
    + getStressorSpecificRegressions
    + Need input file data.SSTV.totabund

# Changes in Version 0.1.0.9034 (2017-06-15)

* Update examples.  Issue #5.
    + getBMIStressorResponses

# Changes in Version 0.1.0.9033 (2017-06-15)

* Update examples.  Issue #5.
    + getBMImatches

# Changes in Version 0.1.0.9032 (2017-06-15)

* Update examples.  Issue #5.
    + getClusterInfo

# Changes in Version 0.1.0.9031 (2017-06-15)

* Update examples.  Issue #5.
    + getStressorList
* Add subdir check to functions that use "Results" subdire.
    + getSiteInfo
    + getChemDataSubsets
    + getStressorList
    + getClusterInfo
    + getAlgStressorResponses
    + getBMIStressorResponses
    + getStressorSpecificRegressions

# Changes in Version 0.1.0.9030 (2017-06-15)

* Update examples.  Issue #5.
    + getChemDataSubsets
* Update data.R.
    + data_Chem
    + data_ChemInfo (update data with GroupName)
    + data_Cluster_Hi

# Changes in Version 0.1.0.9029 (2017-06-15)

* Add vignette.
    + Add package `imager` to Suggests in DESCRIPTION.
    + Basic outline.
    + getSiteInfo function.

# Changes in Version 0.1.0.9028 (2017-06-14)

* GIS data.
    + Standardize projection for GIS layers.
    + getSiteInfo; modify plot and projection used for layers.
* getSiteInfo
    + modify "cluster" data column.
* Examples, change clustertype "H6" to "5"
    + getAlgMatches
    + getAlgStressorResponse
    + getBMIMatches
    + getBMIStressorResponses
    + getCheDataSubsests
    + getClsuterInfo
    + getSiteInfo
    + getStressorList
    + getStressorSpecificRegressions
* data_Sites
    + Modify reference to match code.

# Changes in Version 0.1.0.9027 (2017-06-14)

* Add GIS data.
    + data.R
    + data_GIS_Flow_HI
    + data_GIS_Flow_LO
    + data_GIS_AZ_Outline
* Update getSiteInfo map.
    + Uncomment map code.
    + Change graphics::plot to sp::plot.
* Revised data_SampSummary.
* Revise SampIDs in other files to match format in SampSummary.
    + data_AlgMetrics
    + data_BMIcounts
    + data_BMIMetrics
    + data_Chem

# Changes in Version 0.1.0.9026 (2017-06-12)

* Add data_BMIcounts.
    + Update data.R.
    + Update getStressorSpecificRegressions example.

# Changes in Version 0.1.0.9025 (2017-06-12)

* Modify examples for TargetSite and getSiteInfo.  Issue #5
    + getAlgmatches, getAlgStressorResponses, getBMImatches, getBMIStressorResponses
    , getClusterInfo, getStressorList, getStressorSpecificRegressions.
* Modify examples for file imports vs. included datasets.  Issue #5
    + getAlgmatches, getBMImatches, getClusterInfo, getStressorSpecificRegressions

# Changes in Version 0.1.0.9024 (2017-06-12)

* getChemDataSubset
    + default useLU to FALSE.
    + Error if no cluster information.   Added "stop" condition.

# Changes in Version 0.1.0.9023 (2017-06-11)

* Update example in getChemDataSubset. Issue #5.
    + Create data_ChemInfo
    + Create data_Chem
    + Remove "dontrun" in example.

# Changes in Version 0.1.0.9022 (2017-06-11)

* Add AZ data to "data-raw" and "data". Issue #5.
* getSiteInfo.R
    + Add example datasets (include description in data.R)
    + Turn off mapping.
    + Turn off "donotrun" in example.

# Changes in Version 0.1.0.9021 (2017-06-08)

* Add data requirements to "get" functions in the "details" section.
    + Include column names for required imports
* Add helper function getRegPlotSet.
* Add examples but mark as "dont' run".  Issue #5.
* Add function getAlgMatches.
    + Include return value.

## Changes in Version 0.1.0.9020 (2017-06-07)

* SSDplot
    + Add 3rd dataset so can QC against USEPA ssd generator Excel file.
    + Change proportion formula; rank-0.05 to rank-0.5 to match USEPA
    + Change "Species" to "Taxa" in 2 locations in the code.

## Changes in Version 0.1.0.9019 (2017-06-07)

* Modify format of NEWS file.  Issue #1.

# Changes in Version 0.1.0.9018 (2017-06-06)

* Check issues addressed:
    + Depends R >= 2.1.0
    + no visible global function definition (multiple)
    + Add to Imports; graphics, grDevices, stats, utils
* Check issues not addressed:
    + data_CoOccur, non-ASCII characters in column names.
    + Undocumented object "cluster" in getChemDataSubsets
    + no visible binding for global variable (multiple)
* SSDplot
    + Add second dataset and example.
    + Modify text; font size and justification

# Changes in Version 0.1.0.9017 (2017-06-06)

* Update functions for package dependencies, e.g., readOGR to rgdal::readOGR.
    + getSiteInfo; rgdal
    + getChemDataSubsets; reshape
    + getStressorList; dplyr

# Changes in Version 0.1.0.9016 (2017-06-06)

* Rename SSD function to SSDplot due to conflict with stats::SSD.
* Update CASTfxn.R for function name change.

# Changes in Version 0.1.0.9015 (2017-06-06)

* Fix StressorList return value.  Issue #2.

# Changes in Version 0.1.0.9014 (2017-06-06)

* Fix SSD function.  Issue #3.

# Changes in Version 0.1.0.9013 (2017-06-06)

* Add CASTfxn.R so the package has a help file.

# Changes in Version 0.1.0.9012 (2017-06-06)

* Add function getStressorSpecificRegressions.

# Changes in Version 0.1.0.9011 (2017-06-06)

* Add function getAlgStressorResponses.

# Changes in Version 0.1.0.9010 (2017-06-06)

* Add function getBMIStressorResponses.

# Changes in Version 0.1.0.9009 (2017-06-06)

* Add function getBMImatches.

# Changes in Version 0.1.0.9008 (2017-06-06)

* Add function getStressorList.

# Changes in Version 0.1.0.9007 (2017-06-06)

* Add function getClusterInfo.
* SSD.R
    + Remove "conf=0.95" from qnorm function.

# Changes in Version 0.1.0.9006 (2017-06-06)

* Add function getChemDataSubsets.

# Changes in Version 0.1.0.9005 (2017-06-06)

* Add function getSiteInfo.
* Add Imports to DESCRIPTION.
    + maps
    + maptools
    + raster
    + RColorBrewer
    + reshape
    + rgdal
    + rgeos
    + RgoogleMaps

# Changes in Version 0.1.0.9004 (2017-06-06)

* CoOccur function.
    + Update example.  Remove 2nd Stressors line.
    + Update details from Sue Norton presentation 2017-06-05.

# Changes in Version 0.1.0.9003 (2017-06-05)

* SSD function, non-functional at this point
    + raw data
    + Process raw data script
    + data_SSD.rda in data folder
    + SSD function script
    + data.R, add description of data
* Remove hello function
* Add CoOccur function.
    + raw data
    + process raw data script
    + data_CoOccur in data folder
    + CoOccur script
    + data.R, add description of data

# Changes in Version 0.1.0.9002 (2017-05-27)

* Knit README.RMD so README.md will display on GitHub.

# Changes in Version 0.1.0.9001 (2017-05-27)

* Added basic package structure.
    + Folders (data, data-raw, inst/doc, inst/extdata, man, R, vignettes)
    + NEWS, README
* Update DESCRIPTION, NEWS, and README

# Changes in Version 0.1.0 (2017-05-27)

* Initial commit on GitHub.

