---
title: "CASTfxn Analysis Example"
author: "Erik W. Leppo"
date: "`r Sys.Date()`"
output: 
rmarkdown::html_vignette:
vignette: >
  %\VignetteIndexEntry{Analysis Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
library(knitr)
library(CASTfxn)
```

# Introduction
The generation of output is intended to be accomplished by running a set of SiteIDs through each of the package functions.

The output from each SiteID is created in a folder with the SiteID in the Results folder in the working directory (e.g., "Results/SiteID").

# Example, Site-Specific
Example processing a single site.

Algae data is not used in this example.

SSD plots are not included in the site specific analyses.

Co-Occurrence is not included here either.

```{r Example, eval=FALSE}

# Directory
CurrentDir <- getwd()
myDir.Data <- paste(CurrentDir,"data/",sep="/")
dir_results <- file.path(getwd(), "Results")

predint <- 0.75
varLegLoc <- "topright"

TargetSiteID <- "SRCKN001.61"

# getSiteInfo ####
# dataset inputs
# data, example included with package
data.Stations.Info <- data_Sites
data.SampSummary   <- data_SampSummary
data.303d.ComID    <- data_303d
data.bmi.metrics   <- data_BMIMetrics
data.algae.metrics <- data_AlgMetrics
data.cluster       <- data_Cluster_Hi
data.mod           <- data_ReachMod
data.MT.bmi        <- data_BMIMasterTaxa
# Run getSiteInfo
list.SiteSummary <- getSiteInfo(TargetSiteID)

# getChemDataSubsets ####
# datasets inputs
site.COMID <- list.SiteSummary$COMID
site.Clusters <- list.SiteSummary$ClustIDs
data.chem.raw <- data_Chem
data.chem.info <- data_ChemInfo
# Run getChemDataSubsets
list.data <- getChemDataSubsets(TargetSiteID, site.COMID, site.Clusters)

# getClusterInfo ####
# dataset inputs
ref.reaches <- list.data$ref.reaches
refSiteCOMIDs <- list.data$ref.reaches
# Run getClusterInfo
getClusterInfo(site.COMID, site.Clusters, ref.reaches, dir_results)

# getStressorList ####
# dataset inputs
chem.info <- list.data$chem.info
cluster.chem <- list.data$cluster.chem
cluster.samps <- list.data$cluster.samps
ref.sites <- list.data$ref.sites
site.chem <- list.data$site.chem
# set cutoff for possible stressor identification
probsLow <- 0.10
probsHigh <- 0.90 
# Run getStressorList
list.stressors <- getStressorList(TargetSiteID, site.Clusters, chem.info, cluster.chem
                                 , cluster.samps, ref.sites, site.chem
                                 , probsHigh, probsLow)

# getBMIMatches ####                            
# dataset inputs
## remove "none"
stressors <- list.stressors$stressors[list.stressors$stressors != "none"]
# Run getBMIMatches
list.MatchBMIData <- getBMIMatches(stressors, list.data) 

# getBMIStressorResponses ####
BMIresp <- c("CSCI", "MMI_Score", "TotalTaxSPL_Sc", "DipTaxSPL_Sc"
             , "IntolTaxSPL_Sc", "HBISPL_Sc", "PlecoPct_Sc", "ScrapPctSPL_Sc"
             , "TrichTax_Sc", "EphemTax_Sc", "EphemPct_Sc", "Dom01PctSPL_Sc")
# Run getBMIStressorResponses           
getBMIStressorResponses(TargetSiteID, stressors, BMIresp, list.MatchBMIData)

# getStressorSpecificRegressions ####
# datasets inputs
data.bmi.taxa.raw <- data_BMIcounts
data.SSTV.totabund <- data_BMIRelAbund
# Run getStressorSpecificRegressions
getStressorSpecificRegressions(TargetSiteID
                               , data.SampSummary
                               , data.bmi.taxa.raw
                               , data.chem.info
                               , data.SSTV.totabund
                               , data.MT.bmi
                               , list.MatchBMIData)

# getReport ####
# summary report
dir_results <- file.path(getwd(), "Results")
report_type <- "summary"
report_format <- "html"
getReport(TargetSiteID, dir_results, report_type, report_format)

```

# Co-Occurrence
Not site specific.  Requires a data input file with Biological index scores and all stressors.  The user will need to provide 

```{r CoOccur, eval=FALSE}
#Load Data
df.data <- data_CoOccur
#
col.Group     <- "Group"
col.Bio       <- "CSCI"
col.Stressors <- c("DO_uf_mg_L", "SpecCond_uf_µS_cm", "TN_uf_mg_L", "TP_mg_L")
col.ID        <- c("StationID_Master")
#
Bio.Nar.Brk <- c(-2, 0.62, 0.799, 0.919, 2)
Bio.Nar.Lab <- c("very likely altered", "likely altered"
                , "possibly altered ", "likely intact")
Bio.Deg.Brk <- c(-2, 0.799, 2)
Bio.Deg.Lab <- c("Degraded", "Good")
dir.plots <- file.path(getwd(), "Results")
#
ID.plot <- c("SMC08335", "901SJSJC9", "911TCAM01", "403STC004")
#
getCoOccur(df.data, ID.plot, col.ID, col.Group, col.Bio, col.Stressors
        , Bio.Nar.Brk, Bio.Nar.Lab, Bio.Deg.Brk, Bio.Deg.Lab 
        , dir.plots
        )
```


# Output
It is up to the user to interpret the output of CAST.  CAST is meant as a 
screening tool so the user will need to use best professional judgment to draw
any conclusions.

# Example, Multiple Sites
Example code is below to generate the outputs from each of the CAST functions.
This example uses a mix of the internal example data files and user files.  It is intended as an example, not as functional code.

```{r Output, eval=FALSE}
# Install CASTfxn ####
# library(devtools)
# install_github("ALincolnTt/CASTfxn")

# Set up ####
library(CASTfxn)
library(readxl)

#Dir.Base <- "C:/Users/ann.lincoln/OneDrive - Tetra Tech, Inc/_ActiveProjects/AZ/RCodeData/ChemData"
#Dir.Base <- "P:/Current/OtherGov/City of San Diego/FY2018/CAST_2018/QC_20180705/data"
Dir.Base <- "C:/Users/Erik.Leppo/OneDrive - Tetra Tech, Inc/MyDocs_OneDrive/GitHub/CASTfxn/vignettes/Results"
#setwd("C:\\Users\\Erik.Leppo\\OneDrive - Tetra Tech, Inc\\MyDocs_OneDrive\\GitHub\\CASTfxn_Ann\\CASTfxn")

#Dir.Base <- "C:\\Users\\Erik.Leppo\\OneDrive - Tetra Tech, Inc\\MyDocs_OneDrive\\SanDiego\\Results"
setwd(Dir.Base)

# Site Selection ####
TargetSiteID <- "LCNUT011.29"  # "VRELL009.02"
TargetElevation <- "HI"

# Read Files ####
#Read all data files
data.SampSummary <- data_SampSummary
data.mod         <- data_ReachMod
data.chem.info   <- data_ChemInfo
data.303d.ComID  <- data_303d

# Subset ####
# These need subsetting
if (TargetElevation == "HI") {
    data.cluster   <- data_Cluster_Hi
    fn.coOccur.hi  <- file.path(Dir.Base,"AZCoOccurData_HI.tab")
    data.coOccur   <- read.table(fn.coOccur.hi, header = TRUE, sep = "\t")
    ibi.thresholds <- c(45,52)
} else {
    data.cluster   <- data_Cluster_Lo
    fn.coOccur.lo  <- file.path(Dir.Base, "AZCoOccurData_LO.tab")
    data.coOccur   <- read.table(fn.coOccur.lo, header = TRUE, sep = "\t")
    ibi.thresholds <- c(39,50)
}

# CAST, Stations ####
data.Stations.Info <- data_Sites
data.Stations.Info <- data.Stations.Info[data.Stations.Info$ElevCategory == TargetElevation,]

# CAST, Chem ####
## Use data rather than example file
data.chem.raw <- data_Chem
#
fn.cheminfo2   <- file.path(Dir.Base, "AZStressorInfoFinal.xlsx")
data.chem.info2 <- read_excel(fn.cheminfo2, sheet = 1, skip = 0)
# #
# fn.chem <- file.path(Dir.Base, "AZStressorDataFinal.tab")
# data.chem.raw <- read.delim(fn.chem, na.strings = "NA")
#
analytes      <- data.chem.info$StdParamName[data.chem.info$UseInStressorID == 1]
data.chem.raw <- data.chem.raw[data.chem.raw$StdParamName %in% analytes,]
data.chem.raw <- data.chem.raw[data.chem.raw$ElevCategory == TargetElevation,]

# CAST, BMI, metrics ####
data.bmi.metrics <- data_BMIMetrics
data.bmi.metrics <- data.bmi.metrics[data.bmi.metrics$ElevCategory == TargetElevation,]
data.bmi.metrics <- data.bmi.metrics[data.bmi.metrics$StationID_Master != "VROAK042.78",]
data.bmi.metrics <- data.bmi.metrics[data.bmi.metrics$StationID_Master != "SRHAG007.47",]
data.bmi.metrics <- data.bmi.metrics[,c("StationID_Master","BMISampID",
                                        "BMI.Metrics.SampID","CollDate",
                                        "ElevCategory","NarRat","IBI",
                                        "TotalTaxSPL_Sc","DipTaxSPL_Sc",
                                        "IntolTaxSPL_Sc","HBISPL_Sc","PlecoPct_Sc",
                                        "ScrapPctSPL_Sc","ScrapTaxSPL_Sc",
                                        "TrichTax_Sc","EphemTax_Sc","EphemPct_Sc",
                                        "Dom01PctSPL_Sc")]
data.bmi.metrics <- data.bmi.metrics[, unlist(lapply(data.bmi.metrics, 
                                      function(x) !all(is.na(x))))]

# CAST, Alg, metrics ####
fn.alg.metrics     <- file.path(Dir.Base, "AZAlgaeMetrics.tab")
data.algae.metrics <- read.table(fn.alg.metrics, header = TRUE, sep = "\t")
data.algae.metrics <- data.algae.metrics[!is.na(data.algae.metrics),]

# CAST, misc ####
fn.bmi.raw        <- file.path(Dir.Base, "AZBenthicCountsFinal.tab")
data.bmi.taxa.raw <- read.table(fn.bmi.raw, header = TRUE, sep = "\t")

fn.MT.bmi   <- file.path(Dir.Base, "AZBenthicMasterTaxa.tab")
data.MT.bmi <- read.table(fn.MT.bmi, header = TRUE, sep = "\t", 
                          stringsAsFactors = FALSE)

# read LkpDir (.tab file)
# fn.lkpdir <- "C:/Users/ann.lincoln/OneDrive - Tetra Tech, Inc/_ActiveProjects/AZ/RCodeData/ChemData/AZLkpDir.tab"
# data.lkp.dir <- read.table(fn.lkpdir, header = TRUE, sep = "\t", 
#                            col.names = c("StdParamName","DipTaxSPL_Sc",
#                                          "Dom01PctSPL_Sc","EphemPct_Sc",
#                                          "EphemTax_Sc","HBISPL_Sc","IBI",
#                                          "IntolTaxSPL_Sc","PlecoPct_Sc",
#                                          "ScrapPctSPL_Sc","ScrapTaxSPL_Sc",
#                                          "TotalTaxSPL_Sc","TrichTax_Sc"),
#                            colClasses = c("character","numeric","numeric", 
#                                           "numeric","numeric","numeric","numeric",
#                                           "numeric","numeric","numeric",
#                                           "numeric","numeric","numeric"))
# data.lkp.dir <- data_LkpDir

list.SiteSummary <- getSiteInfo(TargetSiteID)
# Returns: mySiteSummary <- list(SiteInfo = mySiteInfo, Samps = mySamps, 
                                            # BMImetrics = myBMImetrics, 
                                            # AlgMetrics = myAlgaeMetrics, 
                                            # ReachInfo = myReachInfo, 
                                            # COMID = myCOMID, 
                                            # ClustIDs = myClustIDs)
site.COMID <- list.SiteSummary$COMID
site.Clusters <- list.SiteSummary$ClustIDs
SiteInfo <- list.SiteSummary$SiteInfo

list.data <- getChemDataSubsets(TargetSiteID, site.COMID, site.Clusters)
# mySubsets <- list(ref.sites = refSiteIDs, 
                    # ref.reaches = refSiteCOMIDs, 
                    # cluster.samps = cluster.chem.samps, 
                    # chem.info = chems.groups.sort, 
                    # all.chems = all.chems3, 
                    # cluster.chem = cluster.chem.tab5, 
                    # site.chem = site.chem4)
ref.sites <- list.data$ref.sites
ref.reaches <- list.data$ref.reaches
cluster.samps <- list.data$cluster.samps
cluster.chem <- list.data$cluster.chem
site.chem <- list.data$site.chem
chem.info <- list.data$chem.info

# Get Cluster Info
getClusterInfo(site.COMID, site.Clusters, ref.reaches, dir_results)

# CAST, Stressors ####
# Get Stressor List
list.stressors <- getStressorList(TargetSiteID, site.Clusters, chem.info, 
                                  cluster.chem, cluster.samps, ref.sites, 
                                  site.chem, probsHigh=0.75, probsLow=0.25)
# myStressors <- list(stressors = stressorlist, site.stressor.pctrank = site.pctrank)

stressors <- list.stressors$stressors

if ((length(stressors) == 1) && stressors[1] == "none") {
    # No stressors returned
    print(paste("No stressors identified for site", TargetSiteID, sep = " "))
    utils::flush.console()
} else {
  #
    stressors <- c(stressors[2:length(stressors)])
    # Get BMI matches
    list.MatchBMIData <- getBMIMatches(stressors, list.data)
    # myBMIMatchData <- list(all.b.str = all.mbmi.stress
    #                        , cl.b.str = cl.mbmi.stress
    #                        , site.b.str = site.mbmi.stress
    #                        , all.b.rsp = all.mbmi.resp
    #                        , cl.b.rsp = cl.mbmi.resp
    #                        , site.b.rsp = site.mbmi.resp)
        
    # Get BMI Stressor Responses
    getBMIStressorResponses(stressors, list.MatchBMIData)
        
    if (TargetSiteID %in% unique(data.coOccur$StationID_Master)) {
        getCoOccur(data.coOccur, ID.plot=TargetSiteID, col.ID="StationID_Master"
                , col.Group="Group", col.Bio="IBI", col.Stressors=c(stressors)
                , Bio.Nar.Brk=c(0, ibi.thresholds, 100)
                , Bio.Nar.Lab=c("Impaired","Marginal","Good")
                , Bio.Deg.Brk=c(0, min(ibi.thresholds), 100)
                , Bio.Deg.Lab=c("Impaired", "Good"))
    }
        
    # Get Stressor-specific regressions
    predint <- 0.75
    varLegLoc <- "topright"
    myDir.Data <- getwd()
    # read in relative abundance file
    fn.RelAbund <- "AZ_Benthics_RelAbund.xlsx"
    BMIRelAbund <- read_excel(fn.RelAbund, sheet=1)
    #data.SSTV.totabund <- data_BMIRelAbund
    data.SSTV.totabund <- BMIRelAbund
    
    getStressorSpecificRegressions(list.MatchBMIData, predint, varLegLoc)
    # }
    
    # Erik, 20180712, commented out since no data
    # list.MatchAlgData <- getAlgMatches(stressors, list.data)
    # # myAlgMatchData <- list(all.a.str = all.malg.stress
    # #                        , cl.a.str = cl.malg.stress
    # #                        , site.a.str = site.malg.stress
    # #                        , all.a.rsp = all.malg.resp
    # #                        , cl.a.rsp = cl.malg.resp
    # #                        , site.a.rsp = site.malg.resp)
    # 
    # # Get Algal Stressor Responses
    # getAlgStressorResponses(stressors, list.MatchAlgData)

    # getSSDs
    #getSSDplot(Data, ResponseType, Taxa, Exposure)
    myDF <- data_SSD_generator
    myRT   <- "ResponseType"
    myTaxa <- "Taxa"
    myExp  <- "Exposure"
    # Run function
    p3 <- getSSDplot(myDF, myRT, myTaxa, myExp)
    
}
```




