---
title: "Report, Summary"
subtitle: "CAST"
author: "`r Sys.getenv('USERNAME')`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
  pdf_document:
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE)
# Debugging
boo.DEBUG <- FALSE
DEBUG.CaseNumber <- 4
#
# Define pipe
`%>%` <- dplyr::`%>%`
#
if(boo.DEBUG==TRUE){##IF.boo.DEBUG.START
  if(DEBUG.CaseNumber==1){##IF.DEBUG.CaseNumber.START
    TargetSiteID <- "SMC01049"
    dir_results <- "C:/Users/ann.lincoln/Documents/SEP_CAST/Results"
    probsHigh <- 0.75
    probsLow <- 0.25
    report_format="html"
  } else if(DEBUG.CaseNumber==2){
    TargetSiteID <- "907S02774"
    dir_results <- "C:/Users/ann.lincoln/Documents/SEP_CAST/Results"
  } else if(DEBUG.CaseNumber==3){
    TargetSiteID <- "403S01272"
    dir_results <- "C:/Users/ann.lincoln/Documents/SEP_CAST/Results"
  } else if(DEBUG.CaseNumber==4){
    TargetSiteID <- "907S05514"
    dir_data <- "C:/Users/ann.lincoln/Documents/SEP_CAST/Data"
    dir_results <- "C:/Users/ann.lincoln/Documents/SEP_CAST/Results"
    probsHigh <- 0.75
    probsLow <- 0.25
    useAlg <- FALSE
    useBMI <- TRUE
    report_format="html"
    removeOutliers <- TRUE
    useBC <- TRUE # Use Bray-Curtis biological dissimilarity distance matrix
    lagdays=10
    siteQual2Plot = stringr::str_to_sentence("not degraded") # options:"reference","better than","not degraded"
  }##IF.DEBUG.CaseNumber.END
}##IF.boo.DEBUG.END

```

# **REPORT INFORMATION**

```{r report_date}
  myReportDate <- format(Sys.time(), "%Y-%m-%d %H:%M:%S")
  cat(paste("**Report Date and Time:** ",myReportDate,"\n\n",sep=""))
  myUser <- Sys.getenv("USERNAME")
  cat(paste("**Generated By:** ",myUser,"\n\n",sep=""))
  cat(paste("**CASTfxn Package Version:** ",packageVersion("CASTfxn"),"\n\n",sep=""))
  
  cat("**Selected parameters:**\n\n")
  cat(paste("\tRemove outliers? ",removeOutliers,"\n",sep=""))
  cat(paste("\tUse expected biological similarity filter? ",useBC,"\n",sep=""))
  cat(paste("\tNumber of days lag time between stressor and response sample collection = ",lagdays,"\n",sep=""))
  cat(paste("\tQuality of site displayed on analysis graphics? ",siteQual2Plot,"\n",sep=""))
  cat(paste("\tLower and upper quantiles for identifying stressors = ",probsLow
            , "-", probsHigh, "\n",sep=""))
  cat(paste("\tLimit above which DO is not identified as a stressor = ",DOlim
            , "\n",sep=""))
  cat(paste("\tLimits between which pH is not identified as a stressor = ",pHlimLow
            , " and ", pHlimHigh, "\n\n",sep=""))

```

# **SITE INFORMATION**

```{r SiteID}
#list.dirs(file.path(getwd(), "Results"), full.names=FALSE, recursive=FALSE)

  cat(paste("**Site ID:** ",TargetSiteID,"\n\n",sep=""))
```

```{r map, out.width="70%"}
dir.sub3 <- "SiteInfo"
#TargetSiteID <- "SRCKN001.61"
myMAP <- paste0(TargetSiteID,"_MAP.png")
fn_img <- file.path(dir_results, TargetSiteID, dir.sub3, myMAP)
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  cat("No file exists; map.\n")
}
```

## *Site Photos*

```{r photos, out.width="50%", out.extra='style="padding:10px"'}
dir.sub3 <- "SiteInfo"
dir_SiteID <- file.path(dir_results, TargetSiteID, dir.sub3, "Photos")
fn_all  <- list.files(path=dir_SiteID, full.names = TRUE
                                 , pattern=".jpg|.png|.mp4")
txt_grp_msg <- "media"
#
if(length(fn_all)>0){##IF.boo.pdf.START
  msg_files <- paste0("All ", txt_grp_msg," files are in the '"
                      , paste0("Results/",dir.sub3,"/Photos"), "' folder.\n"
                      , "Images are shown here.\n\n")
  cat(msg_files)
  
  fn_Photos_jpg <- fn_all[grep(".jpg", fn_all)]
  
    if(length(fn_Photos_jpg)==0){
      txt_NoFile <- "No file exists; photos.\n"
      cat(txt_NoFile)
    } else if(file.exists(fn_Photos_jpg[1])==TRUE){
      #
      fn_img <- fn_Photos_jpg
      knitr::include_graphics(fn_img)
      #
    } else {
      cat(txt_NoFile)
    }
  
} else if(length(fn_all)==0){
  msg_files <- paste0("No ", txt_grp_msg," files exist.\n")
  
} else {
  msg_files <- ""
  
}##IF.boo.pdf.START
#
```

## *Site Background*

```{r bkgdplots, out.width="80%", out.extra='style="padding:10px"'}
dir.sub3 <- "SiteInfo"
dir_SiteID <- file.path(dir_results, TargetSiteID, dir.sub3)
fn_all  <- list.files(path=dir_SiteID, full.names = TRUE
                                 , pattern=".png")
txt_grp_msg <- "background bar graphs"
#
if(length(fn_all)>0){##IF.boo.pdf.START
  msg_bkg <- paste0("All ", txt_grp_msg," are in the '"
                      , paste0("Results/",dir.sub3), "' folder.\n"
                      , "Selected graphics are shown here.\n\n")
  cat(msg_bkg)
  
  desiredbkg <- c("DevelopLULC", "HousePopul", "Imperv", "StreamMetricsHydro")
  
  fn_bkgd <- fn_all[grep(".png", fn_all)]
  fn_bkgd <- fn_bkgd[grep("BKGD", fn_bkgd)]
  fn_bkgd <- fn_bkgd[grep("DevelopLULC|HousePopul|Imperv|StreamMetricsHydro", fn_bkgd)]
  
    if(length(fn_bkgd)==0){
      txt_NoFile <- "No file exists; background bar plots.\n"
      cat(txt_NoFile)
    } else if(file.exists(fn_bkgd[1])==TRUE){
      #
      fn_img <- fn_bkgd
      knitr::include_graphics(fn_img)
      #
    } else {
      cat(txt_NoFile)
    }
  
} else if(length(fn_all)==0){
  msg_bkg <- paste0("No ", txt_grp_msg," files exist.\n")
  cat(msg_bkg)
  
} else {
  msg_bkg <- ""
  cat(msg_bkg)
  
}##IF.boo.pdf.START
#
```

## *Site Sample Summary*

```{r sampsummary}
# Read file summarizing the comparator data and provide it in summary form

fnSamps <- file.path(dir_data,"SMCSiteSummary.tab")
dfSamps <- read.delim(fnSamps, header=TRUE, sep="\t")
dfSamps <- dfSamps[dfSamps$StationID_Master==TargetSiteID,]
# dfSamps <- data_SampSummary[data_SampSummary$StationID_Master==TargetSiteID,]
row.names(dfSamps) <- NULL
dfSamps <- dplyr::select(dfSamps, -SampYear) %>%
    dplyr::rename(Cluster=clust, SampleDate=SampDate) %>%
    dplyr::mutate(SampleDate=lubridate::mdy(SampleDate))

compscaption <- paste0("Samples collected from ", TargetSiteID, " over time.")
knitr::kable(dfSamps, format=report_format, colnames=colnames(dfSamps)
             , caption = compscaption) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                              , font_size = 12, full_width = FALSE
                              , position = "left") %>%
    kableExtra::column_spec(1,bold = TRUE) %>%
    kableExtra::collapse_rows(columns=1:3, valign="top")
```

# **BMI RESULTS**

## *Biological Index Distributions*

```{r bmi_box}

if(useBMI==TRUE){
    dir.sub3 <- "SiteInfo"
    #TargetSiteID <- "SRCKN001.61"
    myBMIbox <- paste0(TargetSiteID,"_BMI_IndexBoxplots.png")
    fn_img <- file.path(dir_results, TargetSiteID, dir.sub3, myBMIbox)
    if(file.exists(fn_img)==TRUE){
      knitr::include_graphics(fn_img)
    } else {
      cat("No file exists; benthic macroinvertebrate index distributions.\n")
    }
} else {
    cat(paste0("No benthic macroinvertebrate data for ", TargetSiteID,".\n"))
}

```

## *Comparator Site Information*

```{r bmicompsiteinfo}
# Read file summarizing the comparator data and provide it in summary form

if(useBMI==TRUE){
    dir.sub3 <- "SiteInfo"
    mycomps <- paste0(TargetSiteID,"_BMI_SiteQualities.tab")
    fn_comps <- file.path(dir_results, TargetSiteID, dir.sub3, mycomps)
    msg_info <- paste0("Additional comparator site info, "
                       , " including a list of "
                       , "comparator sites can be found in the '"
                       , paste0("Results/",dir.sub3), "' foler.")
    
    if(file.exists(fn_comps)==TRUE){
        cat(msg_info)
        dfcomps <- read.delim(fn_comps, header = TRUE, sep = "\t")
        dfcomps <- dplyr::select(dfcomps, -BioComm)
        compscaption <- paste0("Number of sites by type, group, and quality.")
        knitr::kable(dfcomps, format=report_format, colnames=colnames(dfcomps)
                     , caption = compscaption) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                                      , font_size = 12, full_width = FALSE
                                  , position = "left") %>%
        kableExtra::column_spec(1,bold = TRUE) %>%
        kableExtra::collapse_rows(columns=1:2, valign="top")
    } else {
      cat("No comparator site information is available for benthic macroinvertebrates.\n")
    }    
} else {
    cat(paste0("No benthic macroinvertebrate data for ", TargetSiteID,".\n"))
}

```

## *Potential Candidate Causes*

```{r BMIStrSelect}

if(useBMI==TRUE){
    
    dir.sub3 <- "CandidateCauses"
    fn_stressors <- paste0(TargetSiteID, "_BMI_StressorsEvaluated.tab")
    fn_strUsed <- file.path(dir_results, TargetSiteID, "BMI", dir.sub3, fn_stressors)
      
        if(file.exists(fn_strUsed)){##IF.boo.pdf.START
            dfStrUsed <- read.delim(fn_strUsed, header = TRUE, sep = "\t")
            stressorlist <- paste(as.vector(dfStrUsed[[1]]), collapse = ", ")
            
            msg_strlist <- paste0("Stressors identified as candidate causes include "
                                  , stressorlist, ".\n\n")
        } else if(!file.exists(fn_strUsed)){
            msg_strlist <- paste0("No stressors were identified as possible candidate causes.\n")
        } else {
            msg_strlist <- ""
        }##IF.boo.pdf.START
        #
    cat(msg_strlist)
} else {
    cat(paste0("No benthic macroinvertebrate data for ", TargetSiteID,".\n"))
}
```

```{r files_BMIStrBoxes}

if(useBMI==TRUE){
    dir.sub3 <- "CandidateCauses"
    txt_grp_file <- "CandCauses"
    txt_grp_msg <- "stressor box"
    fn_target <- paste0(TargetSiteID,"_BMI_", txt_grp_file, "_ALL.pdf")
    fn_all <- list.files(file.path(dir_results, TargetSiteID, "BMI", dir.sub3))
    boo_file <- fn_target %in% fn_all
    #
    if(boo_file==TRUE){##IF.boo.pdf.START
      msg_strboxdir <- paste0("All ", txt_grp_msg," plots are in the file '"
                          , fn_target, "' in the'",  paste0("Results/",dir.sub3), "' folder.\n")
    } else if(boo_file==FALSE){
      msg_strboxdir <- paste0("No ", txt_grp_msg," plots exist.\n")
    } else {
      msg_strboxdir <- ""
    }##IF.boo.pdf.START
    #
    cat(msg_strboxdir)

} else {
    cat("")
}

```

```{r BMIStrBoxPlots, out.extra='style="padding:10px"'}

if(useBMI==TRUE){
    dir.sub3 <- "CandidateCauses"
    dir_SiteID <- file.path(dir_results, TargetSiteID, "BMI", dir.sub3)
    fn_BoxPlots  <- list.files(path=dir_SiteID, full.names = TRUE
                                     , pattern="_BMI_CandCauses")
    fn_BoxPlots_jpg <- fn_BoxPlots[grep(".png", fn_BoxPlots)]
    if(length(fn_BoxPlots_jpg)==0){
      txt_NoFile <- "No file exists; box plots.\n"
      cat(txt_NoFile)
    } else if(file.exists(fn_BoxPlots_jpg[1])==TRUE){
      #
      cat(paste("Box plots are arranged by stressor category. Stressors requiring"
                , " further evaluation fall outside the ", probsLow, "-", probsHigh
                , " quantile range.\n\n",sep=""))
    
      fn_img <- fn_BoxPlots_jpg
      knitr::include_graphics(fn_img)
      #
    } else {
      cat(txt_NoFile)
    }
} else {
    cat("")
}

```

## *Weight of Evidence*

### Overall Findings

```{r filelist_WoE_bmi}

if(useBMI==TRUE){
    dir.sub3 <- "WoE"
    dir_WoE_bmi <- file.path(dir_results, TargetSiteID, "BMI", dir.sub3)
    txt_grp_file <- "boxes"
    txt_grp_msg <- "Weight of evidence data"
    fn_target1 <- paste0(TargetSiteID,"_BMI_WoE_ExecSummary.tab")
    fn_target2 <- paste0(TargetSiteID,"_BMI_WoE_ScoresTable.tab")
    fn_target <- c(fn_target1, fn_target2)
    fn_all <- list.files(dir_WoE_bmi)
    boo_file <- all(fn_target %in% fn_all)
    #
    if(boo_file==TRUE){
      msg_files <- paste0(txt_grp_msg," are found in the file '", fn_target
                          , "' in the'", dir_WoE_bmi, "' folder.\n")
    } else if(boo_file==FALSE){
      msg_files <- paste0("No ", txt_grp_msg," exist.\n")
    } else {
      msg_files <- ""
    }
    #
    cat(msg_files)
} else {
    cat("")
}

```

```{r WoEsummary_bmi}

if(useBMI==TRUE){
    dir.sub3 <- "WoE"
    dir_WoE_bmi <- file.path(dir_results, TargetSiteID, "BMI", dir.sub3)
    fn_target1 <- paste0(TargetSiteID,"_BMI_WoE_ExecSummary.tab")
    fn_WoE_ES  <- list.files(path=dir_WoE_bmi, full.names = TRUE
                                     , pattern=fn_target1)
    if(length(fn_WoE_ES)==0){
      txt_NoFile <- "No file exists; weight of evidence summary.\n"
      cat(txt_NoFile)      
    } else if(file.exists(fn_WoE_ES[1])==TRUE){
        df_ES <- read.delim(file.path(dir_WoE_bmi, fn_target1), header=TRUE, sep="\t")
        df_ES <- dplyr::select(df_ES, -BioComm, BioDeg, StressorType, NumStressSamples
                               , NumStressors, WtTot_WoE, WtTotTS_barplot, WtTotCO_boxplot
                               , WtTotSR_InCase_LogRegr, WtTotSR_InCase_LinRegr
                               , WtTotSR_OutCase_LinRegr, WtTotVP_boxplot)
        df_ES <- dplyr::rename(df_ES, SiteID = StationID_Master
                               , Degraded = BioDeg
                               , Group = StressorType
                               , Stressor_Samples = NumStressSamples
                               , Stressors = NumStressors
                               , Overall_WoE = WtTot_WoE
                               , TS_Inside = WtTotTS_barplot
                               , CO_boxplot = WtTotCO_boxplot
                               , SR_Inside_LogRegr = WtTotSR_InCase_LogRegr
                               , SR_Inside_LinRegr = WtTotSR_InCase_LinRegr
                               , SR_Outside_LinRegr = WtTotSR_OutCase_LinRegr
                               , VP_Boxplot = WtTotVP_boxplot)
        df_ES <- dplyr::select(df_ES, SiteID, Degraded, Group, Stressor_Samples
                               , Stressors, Overall_WoE, CO_boxplot
                               , SR_Inside_LogRegr, SR_Inside_LinRegr
                               , SR_Outside_LinRegr, VP_Boxplot)
        EScaption <- paste0("Scores for each line of evidence and overall weight "
                        , "of evidence, weighted by number of stressors in each "
                        , "group.")
        knitr::kable(df_ES, format=report_format, colnames=colnames(df_ES)
                     , caption = EScaption) %>%
            kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                                      , font_size = 12) %>%
            kableExtra::collapse_rows(columns=1:2, valign="top")
    } else {
      cat(txt_NoFile)
    }
} else {
    cat("")
}

```

### Stressor Scores

```{r WoEscores_bmi}

if(useBMI==TRUE){
    dir.sub3 <- "WoE"
    dir_WoE_bmi <- file.path(dir_results, TargetSiteID, "BMI", dir.sub3)
    fn_target2 <- paste0(TargetSiteID,"_BMI_WoE_ScoresTable.tab")
    fn_WoE_det  <- list.files(path=dir_WoE_bmi, full.names = TRUE
                                     , pattern=fn_target2)
    if(length(fn_WoE_det)==0){
      txt_NoFile <- "No file exists; lines of evidence scores\n"
      cat(txt_NoFile)      
    } else if(file.exists(fn_WoE_det[1])==TRUE){
        df_det <- read.delim(file.path(dir_WoE_bmi, fn_target2), header=TRUE, sep="\t")
        df_det <- dplyr::select(df_det, -Cluster, -BioComm, -NumInSupport
                                , -NumInRefute, -NumInIndet, -NumInNotEval
                                , -NumOutSupport, - NumOutRefute, -NumOutIndet
                                , -NumOutNotEval, -StationID_Master)
        df_det <- as.data.frame(unique(df_det))
        df_det <- dplyr::rename(df_det, ResponseSampleID = RespSampID
                                , ResponseSampleDate = RespSampDate
                                , Degraded = BioDeg
                                , Narrative = BioNarrative
                                , StressorSampleID = StressSampID
                                , StressorSampleDate = StressSampDate
                                , Group = StressorType
                                , PercentRank = StressorPctRank
                                , TS_Inside = TS_barplot
                                , SR_Inside_LogRegr = SR_InCase_LogRegr
                                , SR_Inside_LinRegr = SR_InCase_LinRegr
                                , SR_Outside_LinRegr = SR_OutCase_LinRegr
                                , VP_SensitiveTaxa = VP_boxplot_senstaxa
                                , VP_TolerantTaxa = VP_boxplot_toltaxa)
        df_det <- dplyr::mutate(df_det, CSCI = round(CSCI,3)
                                , PercentRank = round(PercentRank, 3)
                                , StressorValue = ifelse(StressorValue<1
                                                         , format(StressorValue
                                                                 , digits=3)
                                                  , ifelse(StressorValue<10
                                                         , format(StressorValue
                                                                 , digits=2)
                                                  , ifelse(StressorValue<100
                                                         , format(StressorValue
                                                                 , digits=1
                                                                 , scientific=FALSE)
                                                         , format(StressorValue
                                                                 , digits=0
                                                                 , big.mark=",")))))
        df_det <- dplyr::select(df_det, Degraded, Narrative, CSCI, ResponseSampleDate
                                , ResponseSampleID, StressorSampleDate
                                , StressorSampleID, Group, Stressor, StressorValue
                                , PercentRank, WoE, TS_Inside, CO_boxplot
                                , SR_Inside_LogRegr, SR_Inside_LinRegr
                                , SR_Outside_LinRegr, VP_SensitiveTaxa
                                , VP_TolerantTaxa, SSD_ToxicityCurve, TotSupport
                                , TotRefute, TotIndet, TotNotEval)
        df_det <- dplyr::arrange(df_det, desc(Degraded), desc(CSCI), StressorSampleDate
                                , ResponseSampleID, StressorSampleID, Group
                                , Stressor, StressorValue)
    
        Detcaption <- paste0("Scores for each line of evidence equal 1 (supports), "
                             , "-1 (refutes), 0 (indeterminate), or NE (not evaluated).")
        knitr::kable(df_det, format=report_format, colnames=colnames(df_det)
                     , caption = Detcaption) %>%
            kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                                      , font_size = 12) %>%
            kableExtra::column_spec(1,bold = TRUE) %>%
            kableExtra::collapse_rows(columns=1:8, valign="top")
    } else {
      cat(txt_NoFile)
    }

} else {
    cat("")
}

```

# **ALGAE RESULTS**

## *Biological Index Distributions*

```{r alg_box}

if(useAlg==TRUE){
    dir.sub3 <- "SiteInfo"
    #TargetSiteID <- "SRCKN001.61"
    myBMIbox <- paste0(TargetSiteID,"_ALGAE_IndexBoxplots.png")
    fn_img <- file.path(dir_results, TargetSiteID, dir.sub3, myBMIbox)
    if(file.exists(fn_img)==TRUE){
      knitr::include_graphics(fn_img)
    } else {
      cat("No file exists; benthic macroinvertebrate index distributions.\n")
    }
} else {
    cat(paste0("No algal data for ", TargetSiteID,".\n"))
}

```

## *Comparator Site Information*

```{r algcompsiteinfo}
# Read file summarizing the comparator data and provide it in summary form

if(useAlg==TRUE){
    dir.sub3 <- "SiteInfo"
    mycomps <- paste0(TargetSiteID,"_ALGAE_SiteQualities.tab")
    fn_comps <- file.path(dir_results, TargetSiteID, dir.sub3, mycomps)
    msg_info <- paste0("Additional comparator site info, including a list of "
                       , "comparator sites can be found in the '"
                       , paste0("Results/",dir.sub3), "' foler.")
    
    if(file.exists(fn_comps)==TRUE){
        cat(msg_info)
        dfcomps <- read.delim(fn_comps, header = TRUE, sep = "\t")
        dfcomps <- dplyr::select(dfcomps, -BioComm)
        compscaption <- paste0("Number of sites by type, group, and quality.")
        knitr::kable(dfcomps, format=report_format, colnames=colnames(dfcomps)
                     , caption = compscaption) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                                      , font_size = 12, full_width = FALSE
                                  , position = "left") %>%
        kableExtra::column_spec(1,bold = TRUE) %>%
        kableExtra::collapse_rows(columns=1:2, valign="top")
    } else {
      cat("No comparator site information is available for benthic macroinvertebrates.\n")
    }    
} else {
    cat(paste0("No algal data for ", TargetSiteID,".\n"))
}

```

## *Potential Candidate Causes*

```{r AlgStrSelect}

if(useAlg==TRUE){
    
    dir.sub3 <- "CandidateCauses"
    fn_stressors <- paste0(TargetSiteID, "_ALGAE_StressorsEvaluated.tab")
    fn_strUsed <- file.path(dir_results,TargetSiteID,"ALGAE",dir.sub3,fn_stressors)
      
        if(file.exists("fn_strUsed")){##IF.boo.pdf.START
            dfStrUsed <- read.delim(fn_strUsed, header = TRUE, sep = "\t")
            stressorlist <- paste(as.vector(dfStrUsed[[1]]), collapse = ", ")
            
            msg_strlist <- paste0("Stressors identified as candidate causes include "
                                  , stressorlist, ".\n\n")
        } else if(!file.exists("fn_strUsed")){
            msg_strlist <- paste0("No stressors were identified as possible candidate causes.\n")
        } else {
            msg_strlist <- ""
        }##IF.boo.pdf.START
        #
    cat(msg_strlist)
} else {
    cat(paste0("No algal data for ", TargetSiteID,".\n"))
}
```

```{r files_AlgStrBoxes}

if(useAlg==TRUE){
    dir.sub3 <- "CandidateCauses"
    txt_grp_file <- "CandCauses"
    txt_grp_msg <- "stressor box"
    fn_target <- paste0(TargetSiteID,"_ALGAE_", txt_grp_file, "_ALL.pdf")
    fn_all <- list.files(file.path(dir_results, TargetSiteID, "ALGAE", dir.sub3))
    boo_file <- fn_target %in% fn_all
    #
    if(boo_file==TRUE){##IF.boo.pdf.START
      msg_strboxdir <- paste0("All ", txt_grp_msg," plots are in the file '"
                          , fn_target, "' in the'", paste0("Results/",dir.sub3)
                          , "' folder.\n")
    } else if(boo_file==FALSE){
      msg_strboxdir <- paste0("No ", txt_grp_msg," plots exist.\n")
    } else {
      msg_strboxdir <- ""
    }##IF.boo.pdf.START
    #
    cat(msg_strboxdir)
} else {
    cat("")
}

```

```{r AlgStrBoxPlots, out.extra='style="padding:10px"'}

if(useAlg==TRUE){
    dir.sub3 <- "CandidateCauses"
    dir_SiteID <- file.path(dir_results, TargetSiteID, "ALGAE", dir.sub3)
    fn_BoxPlots  <- list.files(path=dir_SiteID, full.names = TRUE
                                     , pattern="_ALGAE_CandCauses")
    fn_BoxPlots_jpg <- fn_BoxPlots[grep(".png", fn_BoxPlots)]
    if(length(fn_BoxPlots_jpg)==0){
      txt_NoFile <- "No file exists; box plots.\n"
      cat(txt_NoFile)
    } else if(file.exists(fn_BoxPlots_jpg[1])==TRUE){
      #
      cat(paste("Box plots are arranged by stressor category. Stressors requiring"
                , " further evaluation fall outside the ", probsLow, "-", probsHigh
                , " quantile range.\n\n",sep=""))
    
      fn_img <- fn_BoxPlots_jpg
      knitr::include_graphics(fn_img)
      #
    } else {
      cat(txt_NoFile)
    }
} else {
    cat("")
}

```

## *Weight of Evidence*

### Overall Findings

```{r filelist_WoE_alg}

if(useAlg==TRUE){
    dir.sub3 <- "WoE"
    dir_WoE_alg <- file.path(dir_results, TargetSiteID, "ALGAE", dir.sub3)
    txt_grp_file <- "boxes"
    txt_grp_msg <- "Weight of evidence data"
    fn_target1 <- paste0(TargetSiteID,"_ALGAE_WoE_ExecSummary.tab")
    fn_target2 <- paste0(TargetSiteID,"_ALGAE_WoE_ScoresTable.tab")
    fn_target <- c(fn_target1, fn_target2)
    fn_all <- list.files(dir_WoE_alg)
    boo_file <- all(fn_target %in% fn_all)
    #
    if(boo_file==TRUE){
      msg_files <- paste0(txt_grp_msg," are found in the file '", fn_target
                          , "' in the'", dir_WoE_alg, "' folder.\n")
    } else if(boo_file==FALSE){
      msg_files <- paste0("No ", txt_grp_msg," exist.\n")
    } else {
      msg_files <- ""
    }
    #
    cat(msg_files)
} else {
    cat(paste0("No algal data for ", TargetSiteID,".\n"))
}

```

```{r WoEsummary_alg}

if(useAlg==TRUE){
    dir.sub3 <- "WoE"
    dir_WoE_alg <- file.path(dir_results, TargetSiteID, "ALGAE", dir.sub3)
    fn_target1 <- paste0(TargetSiteID,"_ALGAE_WoE_ExecSummary.tab")
    fn_WoE_ES  <- list.files(path=dir_WoE_alg, full.names = TRUE
                                     , pattern=fn_target1)
    if(length(fn_WoE_ES)==0){
      txt_NoFile <- "No file exists; weight of evidence summary.\n"
      cat(txt_NoFile)      
    } else if(file.exists(fn_WoE_ES[1])==TRUE){
        df_ES <- read.delim(file.path(dir_WoE_alg, fn_target1), header=TRUE, sep="\t")
        df_ES <- dplyr::select(df_ES, -BioComm, BioDeg, StressorType, NumStressSamples
                               , NumStressors, WtTot_WoE, WtTotTS_barplot, WtTotCO_boxplot
                               , WtTotSR_InCase_LogRegr, WtTotSR_InCase_LinRegr
                               , WtTotSR_OutCase_LinRegr, WtTotVP_boxplot)
        df_ES <- dplyr::rename(df_ES, SiteID = StationID_Master
                               , Degraded = BioDeg
                               , Group = StressorType
                               , Stressor_Samples = NumStressSamples
                               , Stressors = NumStressors
                               , Overall_WoE = WtTot_WoE
                               , TS_Inside = WtTotTS_barplot
                               , CO_boxplot = WtTotCO_boxplot
                               , SR_Inside_LogRegr = WtTotSR_InCase_LogRegr
                               , SR_Inside_LinRegr = WtTotSR_InCase_LinRegr
                               , SR_Outside_LinRegr = WtTotSR_OutCase_LinRegr
                               , VP_Boxplot = WtTotVP_boxplot)
        df_ES <- dplyr::select(df_ES, SiteID, Degraded, Group, Stressor_Samples
                               , Stressors, Overall_WoE, TS_Inside, CO_boxplot
                               , SR_Inside_LogRegr, SR_Inside_LinRegr
                               , SR_Outside_LinRegr, VP_Boxplot)
        EScaption <- paste0("Scores for each line of evidence and overall weight "
                        , "of evidence, weighted by number of stressors in each "
                        , "group.")
        knitr::kable(df_ES, format=report_format, colnames=colnames(df_ES)
                     , caption = EScaption) %>%
            kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                                      , font_size = 12) %>%
            kableExtra::collapse_rows(columns=1:2, valign="top")
    } else {
      cat(txt_NoFile)
    }
    
} else {
    cat("")
}

```

### Stressor Scores

```{r WoEscores_alg}

if(useAlg==TRUE){
    dir.sub3 <- "WoE"
    dir_WoE_alg <- file.path(dir_results, TargetSiteID, "ALGAE", dir.sub3)
    fn_target2 <- paste0(TargetSiteID,"_ALGAE_WoE_ScoresTable.tab")
    fn_WoE_det  <- list.files(path=dir_WoE_alg, full.names = TRUE
                                     , pattern=fn_target2)
    if(length(fn_WoE_det)==0){
      txt_NoFile <- "No file exists; lines of evidence scores\n"
      cat(txt_NoFile)      
    } else if(file.exists(fn_WoE_det[1])==TRUE){
        df_det <- read.delim(file.path(dir_WoE_alg, fn_target2), header=TRUE, sep="\t")
        df_det <- dplyr::select(df_det, -Cluster, -BioComm, -NumInSupport
                                , -NumInRefute, -NumInIndet, -NumInNotEval
                                , -NumOutSupport, - NumOutRefute, -NumOutIndet
                                , -NumOutNotEval, -StationID_Master)
        df_det <- as.data.frame(unique(df_det))
        df_det <- dplyr::rename(df_det, ResponseSampleID = RespSampID
                                , ResponseSampleDate = RespSampDate
                                , Degraded = BioDeg
                                , Narrative = BioNarrative
                                , StressorSampleID = StressSampID
                                , StressorSampleDate = StressSampDate
                                , Group = StressorType
                                , PercentRank = StressorPctRank
                                , TS_Inside = TS_barplot
                                , SR_Inside_LogRegr = SR_InCase_LogRegr
                                , SR_Inside_LinRegr = SR_InCase_LinRegr
                                , SR_Outside_LinRegr = SR_OutCase_LinRegr
                                , VP_SensitiveTaxa = VP_boxplot_senstaxa
                                , VP_TolerantTaxa = VP_boxplot_toltaxa)
        df_det <- dplyr::mutate(df_det, MMIhybrid = round(MMIhybrid,3)
                                , PercentRank = round(PercentRank, 3)
                                , StressorValue = ifelse(StressorValue<1
                                                         , format(StressorValue
                                                                 , digits=3)
                                                  , ifelse(StressorValue<10
                                                         , format(StressorValue
                                                                 , digits=2)
                                                  , ifelse(StressorValue<100
                                                         , format(StressorValue
                                                                 , digits=1
                                                                 , scientific=FALSE)
                                                         , format(StressorValue
                                                                 , digits=0
                                                                 , big.mark=",")))))
        df_det <- dplyr::select(df_det, Degraded, Narrative, MMIhybrid
                                , ResponseSampleDate, ResponseSampleID
                                , StressorSampleDate, StressorSampleID, Group
                                , Stressor, StressorValue, PercentRank, WoE
                                , TS_Inside, CO_boxplot, SR_Inside_LogRegr
                                , SR_Inside_LinRegr, SR_Outside_LinRegr
                                , VP_SensitiveTaxa, VP_TolerantTaxa
                                , SSD_ToxicityCurve, TotSupport, TotRefute
                                , TotIndet, TotNotEval)
        df_det <- dplyr::arrange(df_det, desc(Degraded), desc(MMIhybrid)
                                , StressorSampleDate, ResponseSampleID
                                , StressorSampleID, Group, Stressor, StressorValue)
    
        Detcaption <- paste0("Scores for each line of evidence equal 1 (supports), "
                             , "-1 (refutes), 0 (indeterminate), or NE (not evaluated).")
        knitr::kable(df_det, format=report_format, colnames=colnames(df_det)
                     , caption = Detcaption) %>%
            kableExtra::kable_styling(bootstrap_options = c("striped","condensed")
                                      , font_size = 12) %>%
            kableExtra::column_spec(1,bold = TRUE) %>%
            kableExtra::collapse_rows(columns=1:8, valign="top")
    } else {
      cat(txt_NoFile)
    }

} else {
    cat("")
}

```





