---
title: "Report, Summary"
subtitle: "CAST"
author: "`r Sys.getenv('USERNAME')`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
  pdf_document:
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE)
#TargetSiteID <- "SRCKN001.61"
# dir_results <- "C:\\Users\\Erik.Leppo\\OneDrive - Tetra Tech, Inc\\MyDocs_OneDrive\\GitHub\\CASTfxn\\Results"
# TargetSiteID <- "LCBIL000.15"
# dir_results <- "C:/Users/Erik.Leppo/OneDrive - Tetra Tech, Inc/MyDocs_OneDrive/AZ/"
```

# REPORT INFORMATION

```{r report_date}
  myReportDate <- format(Sys.time(), "%Y-%m-%d %H:%M:%S")
  cat(paste("**Report Date and Time:** ",myReportDate,"\n\n",sep=""))
  myUser <- Sys.getenv("USERNAME")
  cat(paste("**Generated By:** ",myUser,"\n\n",sep=""))
  cat(paste("**CASTfxn Package Version:** ",packageVersion("CASTfxn"),"\n\n",sep=""))
```

# SITE INFORMATION

```{r SiteID}
#list.dirs(file.path(getwd(), "Results"), full.names=FALSE, recursive=FALSE)

  cat(paste("**Site ID:** ",TargetSiteID,"\n\n",sep=""))
```

# MAP

```{r map}
#TargetSiteID <- "SRCKN001.61"
myJPG <- paste0(TargetSiteID,".map.jpg")
fn_img <- file.path(dir_results, TargetSiteID, myJPG)
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  cat("No file exists; map.\n")
}
```

# BOX PLOTS

Box plots by stressor category.

```{r BoxPlots}
dir_SiteID <- file.path(dir_results, TargetSiteID)
fn_BoxPlots  <- list.files(path=dir_SiteID, full.names = TRUE
                                 , pattern=".boxes.")
fn_BoxPlots_jpg <- fn_BoxPlots[grep(".jpg", fn_BoxPlots)]
if(length(fn_BoxPlots_jpg)==0){
  txt_NoFile <- "No file exists; box plots.\n"
  cat(txt_NoFile)
} else if(file.exists(fn_BoxPlots_jpg[1])==TRUE){
  #
  fn_img <- fn_BoxPlots_jpg
  knitr::include_graphics(fn_img)
  #
} else {
  cat(txt_NoFile)
}
```


# STRESSOR RESPONSE

## BMI

### Tables

Correlograms instead of long tables are used to visually display the stressor and response metrics for correlations and scores.

#### Correlations

```{r SR_BMI_corrs}
fn_SR_BMI_Corrs  <- file.path(dir_results, TargetSiteID
                              , paste0(TargetSiteID, ".SR.BMI.Corrs.txt"))
# fn_SR_BMI_Scores <- file.path(dir_results, TargetSiteID
#                               , paste0(TargetSiteID, ".SR.BMI.Scores.txt"))
#
# captions
cap_SR_BMI_Corrs  <- "Stressor Response, BMI, Correlations"
# cap_SR_BMI_Scores <- "Stressor Response, BMI, Scores"
#
# Corrs
if(file.exists(fn_SR_BMI_Corrs)==TRUE){##IF.corrs.START
  cat(paste0("\n", cap_SR_BMI_Corrs,"\n"))
  df_SR_BMI_Corrs <- read.delim(fn_SR_BMI_Corrs)
  # Plot
  df_corr_r <- reshape2::dcast(df_SR_BMI_Corrs, stressName ~ respName, value.var="estimate")
  df_corrplot <- t(df_corr_r[,-1])
  colnames(df_corrplot) <- df_corr_r[,1]
  corrplot::corrplot(df_corrplot, method="circle")
} else {
  cat("No file exists; Stressor Response BMI correlations.\n")
}

# # Table, Corrs
# if(file.exists(fn_SR_BMI_Corrs)==TRUE){##IF.corrs.START
#   df_SR_BMI_Corrs <- read.delim(fn_SR_BMI_Corrs)
#   # Table
#   print(knitr::kable(df_SR_BMI_Corrs, caption=cap_SR_BMI_Corrs))
# } else {
#   cat("No file exists; Stressor Response BMI correlations.\n")
# }##IF.corrs.START


# # Scores
# if(file.exists(fn_SR_BMI_Scores)==TRUE){##IF.scores.START
#   cat(paste0("\n#### ", cap_SR_BMI_Scores,"\n"))
#   df_SR_BMI_Scores <- read.delim(fn_SR_BMI_Scores)
#   #knitr::kable(df_SR_BMI_Scores, caption=cap_SR_BMI_Scores)
#   df_score <- reshape2::dcast(df_SR_BMI_Scores, Param_Name ~ BMI_Metric, value.var="SR_Score")
#   df_corrplot <- t(df_score[,-1])
#   colnames(df_corrplot) <- df_score[,1]
#   corrplot::corrplot(df_corrplot, is.corr=FALSE, method="circle")
# } else {
#   cat("No file exists; Stressor Response BMI scores.\n")
# }##IF.scores.START
```

#### Scores

```{r SR_BMI_scores}
# fn_SR_BMI_Corrs  <- file.path(dir_results, TargetSiteID
#                               , paste0(TargetSiteID, ".SR.BMI.Corrs.txt"))
fn_SR_BMI_Scores <- file.path(dir_results, TargetSiteID
                              , paste0(TargetSiteID, ".SR.BMI.Scores.txt"))
#
# captions
# cap_SR_BMI_Corrs  <- "Stressor Response, BMI, Correlations"
cap_SR_BMI_Scores <- "Stressor Response, BMI, Scores"
#
# # Corrs
# if(file.exists(fn_SR_BMI_Corrs)==TRUE){##IF.corrs.START
#   cat(paste0("\n#### ", cap_SR_BMI_Corrs,"\n"))
#   df_SR_BMI_Corrs <- read.delim(fn_SR_BMI_Corrs)
#   # Plot
#   df_corr_r <- reshape2::dcast(df_SR_BMI_Corrs, stressName ~ respName, value.var="estimate")
#   df_corrplot <- t(df_corr_r[,-1])
#   colnames(df_corrplot) <- df_corr_r[,1]
#   corrplot::corrplot(df_corrplot, method="circle")
# }
# 
# # # Table, Corrs
# # if(file.exists(fn_SR_BMI_Corrs)==TRUE){##IF.corrs.START
# #   df_SR_BMI_Corrs <- read.delim(fn_SR_BMI_Corrs)
# #   # Table
# #   print(knitr::kable(df_SR_BMI_Corrs, caption=cap_SR_BMI_Corrs))
# # } else {
# #   cat("No file exists; Stressor Response BMI correlations.\n")
# # }##IF.corrs.START


# Scores
if(file.exists(fn_SR_BMI_Scores)==TRUE){##IF.scores.START
  cat(paste0("\n", cap_SR_BMI_Scores,"\n"))
  df_SR_BMI_Scores <- read.delim(fn_SR_BMI_Scores)
  #knitr::kable(df_SR_BMI_Scores, caption=cap_SR_BMI_Scores)
  df_score <- reshape2::dcast(df_SR_BMI_Scores, Param_Name ~ BMI_Metric, value.var="SR_Score")
  df_corrplot <- t(df_score[,-1])
  colnames(df_corrplot) <- df_score[,1]
  corrplot::corrplot(df_corrplot, is.corr=FALSE, method="circle")
} else {
  cat("No file exists; Stressor Response BMI scores.\n")
}##IF.scores.START
```

### Plots

```{r SR_BMI_plots}
fn_SR_BMI_Corrs  <- file.path(dir_results, TargetSiteID
                              , paste0(TargetSiteID, ".SR.BMI.Corrs.txt"))
#
if(file.exists(fn_SR_BMI_Corrs)==TRUE){
  df_SR_BMI_Corrs <- read.delim(fn_SR_BMI_Corrs)
  Corr_Analyte <- sort(unique(df_SR_BMI_Corrs$stressName))
  fn_img <- list.files(file.path(dir_results, TargetSiteID)
                     , paste0(TargetSiteID,".SR.BMI.", Corr_Analyte), full.names = TRUE)
  knitr::include_graphics(fn_img)
} else {
  cat("No file exists; Stressor Response BMI correlation plots.\n")
}
#

```

## SSTV

### Table

```{r SR_SSTV_tables}
fn_SR_SSTV_Corrs  <- file.path(dir_results, TargetSiteID
                               , paste0(TargetSiteID, ".SR.SSTV.Corrs.txt"))

cap_SR_SSTV_Corrs <- "Stressor Response, SSTV, Correlations"
  
# Table
if(file.exists(fn_SR_SSTV_Corrs)==TRUE){
  #
  df_SR_SSTVCorrs <- read.delim(fn_SR_SSTV_Corrs)
  # Table
 # print(knitr::kable(df_SR_SSTVCorrs, caption=cap_SR_SSTV_Corrs))
  #
  cat(paste0("\n", cap_SR_SSTV_Corrs,"\n"))
  #
  df_SR_SSTVCorrs <- read.delim(fn_SR_SSTV_Corrs)
  # Plot
  df_corr_r <- reshape2::dcast(df_SR_SSTVCorrs, stressName ~ respName, value.var="estimate")
  df_corrplot <- t(df_corr_r[,-1])
  colnames(df_corrplot) <- df_corr_r[,1]
  corrplot::corrplot(df_corrplot, method="circle")
} else {
  cat("No file exists; Stressor Response SSTV data.\n")
}

# Plot
if(file.exists(fn_SR_SSTV_Corrs)==TRUE){
  #
 
  #
}

```

## Algae

### Tables

Correlograms instead of long tables are used to visually display the stressor and response metrics for correlations and scores.

#### Correlations

```{r SR_Alg_corrs}
fn_SR_Alg_Corrs  <- file.path(dir_results, TargetSiteID
                              , paste0(TargetSiteID, ".SR.Alg.Corrs.txt"))

# captions
cap_SR_Alg_Corrs  <- "Stressor Response, Algae, Correlations"

# Corrs
if(file.exists(fn_SR_Alg_Corrs)==TRUE){##IF.corrs.START
  cat(paste0("\n", cap_SR_Alg_Corrs,"\n"))
  df_SR_Alg_Corrs <- read.delim(fn_SR_Alg_Corrs)
  # Plot
  df_corr_r <- reshape2::dcast(df_SR_Alg_Corrs, stressName ~ respName, value.var="estimate")
  df_corrplot <- t(df_corr_r[,-1])
  colnames(df_corrplot) <- df_corr_r[,1]
  corrplot::corrplot(df_corrplot, method="circle")
} else {
  cat("No file exists; Stressor Response Algae correlations.\n")
}

```

# OTHER

## Co-Occurence

### Table

```{r CoOccur_tables}
#dir_results <- file.path(getwd(), "Results", "_CoOccur", "hi")
# dir_SiteID <- file.path(dir_results, TargetSiteID)

fn_CoOccur_Scores  <- list.files(path=file.path(dir_results, TargetSiteID)
                                 , full.names = TRUE
                                 , pattern=".CoOccurrence.Scores.")
if(length(fn_CoOccur_Scores)==0){
  txt_NoFile <- "No file exists; co-occurrence scores.\n"
  cat(txt_NoFile)
} else if(file.exists(fn_CoOccur_Scores)==TRUE){
  df_CoOccur_Scores <- read.delim(fn_CoOccur_Scores)
  cap_CoOccur_Scores <- "Co-Occurrence Scores"
  knitr::kable(df_CoOccur_Scores, caption=cap_CoOccur_Scores)
} else {
  cat(txt_NoFile)
}
#
```

### Plots

Plots are saved from the function in pairs in a PDF.

* SiteID.CoOccurrence.YYYYMMDD_HHMMSS.pdf

## Chem, Percent Rank

### Table

```{r ChemPctRank_table}
fn_ChemPctRank  <- file.path(dir_results, TargetSiteID
                               , paste0(TargetSiteID, ".chem.pctrank.txt"))

if(file.exists(fn_ChemPctRank)==TRUE){
  df_ChemPctRank <- read.delim(fn_ChemPctRank)
  cap_ChemPctRank <- "Chemical Analytes, Percent Rank"
  knitr::kable(df_ChemPctRank, caption=cap_ChemPctRank)
} else {
  cat("No files exists; chemistry percent ranks.\n")
}
```

