---
title: "CASTool"
subtitle: "Full Report"
author: "`r Sys.getenv('USERNAME')`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  pdf_document:
    toc: true
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  markdown: 
    wrap: 72
---

<!-- #  Copyright 2025 TetraTech. All rights reserved. -->

<!-- #  Use, copying, modification, or distribution of this file or any of its contents  -->

<!-- #  is expressly prohibited without prior written permission of TetraTech. -->

<!-- # Embed logo -->

<img src="CASTool.svg" style="position:absolute; top:0px; right:0px; padding:10px;"/>

<!-- # Add css for vertical alignment of table header cells -->

<head>

```{=html}
<style type="text/css">
    <!-- .dt-left {horizontal-align: left;} -->
    <!-- .dt-center {horizontal-align: center;} -->
    <!-- .dt-right {horizontal- align: right;} -->
    .dt-top {vertical-align: top;}
    .dt-middle {vertical-align: middle;}
    .dt-bottom {vertical-align: bottom;}
  </style>
```

</head>

```{r setup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(results = 'asis', echo = FALSE, warning = FALSE)
# Debugging
# boo.DEBUG <- TRUE
# DEBUG.CaseNumber <- 1
#
# Define pipe and not_all_na
`%>%` <- dplyr::`%>%`
not_all_na <- function(x) {!all(is.na(x))}

#
# if (boo.DEBUG == TRUE) {##IF.boo.DEBUG.START
#   if (DEBUG.CaseNumber == 1) {##IF.DEBUG.CaseNumber.START
#     TargetSiteID <- "WAM06600_003688"
#     dir_data <- dir_data
#     dir_results <- dir_results
#   }##IF.DEBUG.CaseNumber.END
# }##IF.boo.DEBUG.END

```

# **DISCLAIMER**

The Causal Assessment Screening Tool (CASTool) is designed to assess
causes of biological impairment. CASTool is a data-driven tool that
relies on the quality and completeness of the biological response and
candidate stressor data provided by the user. It is most appropriately
used to identify candidate causes which merit additional evaluation. The
conceptual framework for the CASTool is the U.S. Environmental
Protection Agency’s Causal Analysis/Diagnosis Decision Information
System (CADDIS), which can be consulted for additional information on
causal assessment.

# **Target Site: `r TargetSiteID`**
## **Region: `r regionName`**

## **Parameterization**

```{r report_date, echo = FALSE}

  biocomms <- tolower(biocommlist)
  if (length(biocommlist) > 1) {
    biocomms <- toString(biocommlist[1:length(biocommlist) - 1])
    biocomms <- paste(biocomms, biocommlist[length(biocommlist)],
                      sep = " and ")
  }
  biocomms <- sub("bmi", "benthic macroinvertebrates", biocomms)
  biocomms <- sub("alg", "algae", biocomms)
  
  lagdays <- paste(lagdays, collapse = ", ")

  cat(paste("**Biological communities evaluated:** ", biocomms, "\n\n", sep = ""))
  # cat(paste("**Primary biological indices used for degraded/not degraded determination:** ", 
  #           primeIndex, "\n\n", sep = ""))
  # cat(paste("\t**Secondary biological indices used to generate supplemental figures: **", 
  #           bioIndex, "\n", sep = ""))
  cat(paste("**Remove outliers:** ", removeOutliers, "\n\n", sep = ""))
  cat(paste("**Use expected biological similarity filter:** ", useBC, "\n\n", sep = ""))
  cat(paste("**Minimum number of samples to identify candidate causes:** ", samplim, 
            "\n\n", sep = ""))
  cat(paste("**Number of allowable lag days between stressor and response measurements:** -",
            lagdays, "\n\n", sep = ""))
  cat(paste("**R2 cutoff:** ", r2_cutoff, "\n\n", sep = ""))
  cat(paste("**p-value cutoff:** ", p.val_cutoff, "\n\n", sep = ""))
  cat(paste("**Cluster assignment file:** ", basename(fn.cluster), "\n", sep = ""))

```

## **Target site information**

### *Site map*

```{r map, out.width = "80%", echo = FALSE}

dir.sub <- "SiteInfo"
myMAP <- paste0(TargetSiteID,"_map.png")
fn_img <- file.path(dir_results, TargetSiteID, dir.sub, myMAP)

if (file.exists(fn_img) == TRUE) {
  knitr::include_graphics(fn_img)
} else {
  cat("No file exists; map.\n")
}

```

### *Site photo(s)*

```{r photos, out.width = "50%", echo = FALSE}

dir.sub <- "SiteInfo"
dir_SiteID <- file.path(dir_results, TargetSiteID, dir.sub, "Photos")
fn_all  <- list.files(path = dir_SiteID, full.names = TRUE,
                      pattern = ".jpg|.png|.mp4")

txt_grp_msg <- "media"
#
if (length(fn_all) > 0) {##IF.Media
  msg_files <- paste0("All media ", txt_grp_msg," files are in the '",
                      paste0("Results/", TargetSiteID, "/", dir.sub, "/Photos"), 
                      "' folder.\n", "Static photos are shown here.\n\n")
  cat(msg_files)
  
  fn_Photos_jpg <- fn_all[grep("[.jpg|.png]", fn_all)]
  
  for (p in seq_along(fn_Photos_jpg)) {
    fn <- fn_Photos_jpg[p]
    cat(paste0("<img src = ", fn, " />"))
  }
  
} else {
  
  msg_files <- paste0("No ", txt_grp_msg," files exist.\n")
  cat(msg_files)
  
}##IF.Media.END

```

### *Target site sample summary*

The table below lists any samples collected from `r TargetSiteID` over
time. Index scores are followed by their biological quality for benthic
macroinvertebrates (`r ifelse(!is.null(bmiIndex), bmiIndex, "N/A")`),
algae (`r ifelse(!is.null(algIndex), algIndex, "N/A")`), or fish
(`r ifelse(!is.null(fishIndex), fishIndex, "N/A")`).

```{r sampsummary, echo = FALSE}

# Read file summarizing the sample data and provide it in summary form
dfSamps <- data_sampSummary[data_sampSummary$StationID == TargetSiteID, ]
TScomid <- unique(dfSamps$COMID)
TScluster <- ifelse(useBC == TRUE, 
                    unique(dfSamps$OutcaseCol), 
                    unique(dfSamps$IncaseCol))

row.names(dfSamps) <- NULL

camelCaseToTitleCase <- function(camelCaseString) {
  # Insert spaces before uppercase letters (except the first character)
  tempString <- gsub("([A-Z])", " \\1", camelCaseString)
  
  # Capitalize the first letter of each word and convert the rest to lowercase
  # This handles the case where the original string starts with an uppercase
  # letter and ensures subsequent words are correctly capitalized.
  titleCaseString <- tools::toTitleCase(tempString)
  
  # Remove any leading spaces that might have been introduced if the original
  # string started with an uppercase letter
  titleCaseString <- trimws(titleCaseString)
  
  # Join "I D" to recreate "ID"
  titleCaseString <- sub("(I D)", "ID", titleCaseString)
  
  # Join "B M I" to recreate "BMI"
  titleCaseString <- sub("(B M I)", "BMI", titleCaseString)
  
  return(titleCaseString)
}

# Get sample data
if (nrow(dfSamps) > 0) {# Samples exist for target site
  
  dfSamps <- dplyr::select(dfSamps, !c(StationID, COMID, OutcaseCol, IncaseCol)) %>%
    tidyr::pivot_longer(cols = -SampleDate, names_to = "ColName", values_to = "Content") %>%
    dplyr::mutate(ColName = camelCaseToTitleCase(ColName)) %>%
    tidyr::pivot_wider(id_cols = SampleDate, names_from = ColName, values_from = Content)
  
  # Get response data
  if (!is.null(data_bmiMetrics)) {
    origcol <- which(colnames(dfSamps) == "BMI Sample ID")
    dfbmi <- dplyr::filter(data_bmiMetrics, StationID == TargetSiteID) %>%
      dplyr::select(RespSampleID, all_of(bmiIndex), Quality)
    dfSamps <- merge(dfSamps, dfbmi, by.x = "BMI Sample ID", by.y = "RespSampleID",
                     all.x = TRUE)
    dfSamps <- dplyr::rename(dfSamps, `BMI Quality` = Quality)
    dfSamps <- dfSamps[, c(2:(origcol), 1, (origcol + 1):ncol(dfSamps))]
  }
  if (!is.null(data_algMetrics)) {
    origcol <- which(colnames(dfSamps) == "Algae Sample ID")
    dfalg <- dplyr::filter(data_algMetrics, StationID == TargetSiteID) %>%
      dplyr::select(RespSampleID, all_of(algIndex), Quality)
    dfSamps <- merge(dfSamps, dfalg, by.x = "Algae Sample ID", by.y = "RespSampleID",
                     all.x = TRUE)
    dfSamps <- dplyr::rename(dfSamps, `Algae Quality` = Quality)
    dfSamps <- dfSamps[, c(2:(origcol), 1, (origcol + 1):ncol(dfSamps))]
  }
  if (!is.null(data_fishMetrics)) {
    origcol <- which(colnames(dfSamps) == "Fish Sample ID")
    dffish <- dplyr::filter(data_fishMetrics, StationID == TargetSiteID) %>%
      dplyr::select(RespSampleID, all_of(fishIndex), Quality)
    dfSamps <- merge(dfSamps, dffish, by.x = "Fish Sample ID", by.y = "RespSampleID",
                     all.x = TRUE)
    dfSamps <- dplyr::rename(dfSamps, `Fish Quality` = Quality)
    dfSamps <- dfSamps[, c(2:(origcol), 1, (origcol + 1):ncol(dfSamps))]
  }
  
  tblColNames <- colnames(dfSamps)
  
  if (report_format == "html") {
    
    tblCaption <- paste0("Samples collected from ", TargetSiteID,".")

    DT::datatable(dfSamps,
                  extensions = 'FixedColumns',
                  # caption = tblCaption,
                  options = list(layout = list(top1 = list(id = 'cellID',
                                                          className = 'cellClass',
                                                          features = list(
                                                            # div = list(
                                                              text = tblCaption)
                                                            # )
                                                          ),
                                               topStart = 'pageLength',
                                               topEnd = 'search',
                                               bottomStart = 'info',
                                               bottomEnd = 'paging'),
                                 pageLength = 10,
                                 menu = ifelse(nrow(dfSamps) > 10,
                                               c(10, 25, 50, 100), 10),
                                 bSort = FALSE,
                                 scrollX = TRUE,
                                 fixedColumns = TRUE,
                                 columnDefs = list(list(className = 'dt-center',
                                                        targets = '_all'),
                                                   list(className = 'dt-bottom',
                                                        targets = '_all'))),
                  colnames = tblColNames,
                  class = 'striped hover row-border',
                  filter = 'none',
                  rownames = FALSE) %>%
      DT::formatStyle(columns = colnames(dfSamps), fontSize = '85%') 
    
  } else {
    
    msg <- "Not displayed in non-html format."
    cat(msg)
    
  }

} else {
  
  cat(paste0("No sample data for ", TargetSiteID))
  
}

```

### *Comparator sites*

Comparator sites will depend upon several factors:

-   which version of the regional clustering file is used
-   whether or not an alternate method is used to assign comparator
    sites
-   whether or not a Bray-Curtis dissimilarity distance matrix is
    included in the evaluation

Comparator samples have a quality associated with them, that differs
based on the biological community index used. For these, please see the
biological community comparator samples section.

### *Watershed stressor summaries*

The downloadable zip file contains figures summarizing watershed
attributes of the target site compared to all reaches inside the case.
These figures may provide additional insight into causes of stream
impairment. For example, if nitrogen species were not measured and
provided to the CASTool, a relatively high (NNI var) may indicate that
nitrogen pollution merits additional scrutiny as a potential candidate
cause of impairment.

## **Benthic macroinvertebrate results**

### *Index summary*

```{r bmiIdxGraph, out.width = "75%", echo = FALSE}
dir.sub3 <- "SiteInfo"
fn_bmiIndexGraphic <- file.path(dir_results, TargetSiteID, dir.sub3, 
                                paste0(TargetSiteID, 
                                       "_BMI_IndexBoxplotsByCase.png"))
#
if ("bmi" %in% biocommlist) {
  
  if (file.exists(fn_bmiIndexGraphic)) {##IF.boo.pdf.START
    msg_files <- paste0("This image file is in the '",
                        paste0("Results/", dir.sub3, "' folder.\n\n"))
    cat(msg_files)
  
    knitr::include_graphics(fn_bmiIndexGraphic)  
  } else {
  
    msg_files <- "The BMI summary image file is not accessible."
    cat(msg_files)
  
  }
  
} else {
  
  cat("Benthic macroinvertebrate data were not evaluated.")
}


```

### *Comparator sample summary*

Comparator samples are also called "inside-the-case" samples. In
contrast, "outside-the-case" samples may be all the samples in the
region or a subset thereof. The following table includes sample quality,
which may differ between biological communities.

```{r bmi_compsites, echo = FALSE, out.extra = 'style = "padding:10px"'}
# Read file summarizing the comparator data and provide it in summary form

if ("bmi" %in% biocommlist) {
  dir.sub3 <- "SiteInfo"
  mycomps <- paste0(TargetSiteID, "_BMI_SiteQualities.tab")
  fn_comps <- file.path(dir_results, TargetSiteID, dir.sub3, mycomps)
  msg_info <- paste0("Comparator site information, including a list ",
                     "of comparator sites, can be found in the '",
                     paste0(paste0("Results/", TargetSiteID, "/", dir.sub3),
                            "' folder."), "\n\n")

  if (file.exists(fn_comps) == TRUE) {
    
    dfcomps <- read.delim(fn_comps, header = TRUE, sep = "\t")
    dfcomps <- dplyr::select(dfcomps, -BioComm) %>%
      dplyr::rename(`Inside-the-case samples` = InsideCaseSamples,
                    `Outside-the-case samples` = OutsideCaseSamples,
                    `Reference samples` = ReferenceSamples,
                    `Total samples` = AllSamples)
    
    cat(msg_info)
    
    tcomps <- knitr::kable(dfcomps, format = report_format,
                           colnames = colnames(dfcomps))
    tcomps <- kableExtra::kable_styling(tcomps,
                                        bootstrap_options = "condensed",
                                        font_size = 12, full_width = FALSE,
                                        position = "left")
    tcomps
  } else {
    cat(paste0("The file ", mycomps, " is not accessible.\n"))
  }
} else {
    cat(paste0("No benthic macroinvertebrate data are available for ", TargetSiteID,".\n"))
}

```

### *Candidate causes*

#### User-specified thresholds:

-   DO lower limit that automatically triggers further evaluation \<=
    `r DOlim`
-   pH lower limit that automatically triggers further evaluation \<=
    `r pHlimLow`
-   pH upper limit that automatically triggers further evaluation \>=
    `r pHlimHigh`

#### Stressor(s) initially evaluated:

Stressors identified for initial evaluation include any that are
detected in the target site *and* marked as "use in stressor id" in the
stressor metadata.

```{r bmi_stressordetects, echo = FALSE}

  siteDetects <- data_stressInfo %>%
    dplyr::filter(StdParamName %in% siteDetectsAll) %>%
    dplyr::select(Label)
  siteDetects <- unlist(siteDetects)
  bullet <- "\U2022"

  if (length(siteDetects) > 0) {
    for (s in siteDetects) {
      cat(paste0(bullet, " ", s, "\n\n"))
    }
  } else {
    cat("No stressors were detected in any samples from the target site.")
  }

```

#### Stressor(s) eliminated by comparison of target and comparator site values:

```{r bmi_stressorNE, echo = FALSE}

if ("bmi" %in% biocommlist) {
  dir.sub3 <- "_WoE"
  fnNE <- paste0(TargetSiteID, "_BMI_DetectsNotEvalFurther.tab")
  fnNE <- file.path(dir_results, TargetSiteID, "BMI", dir.sub3, fnNE)
  
  if (file.exists(fnNE)) {
    notEvaluated <- read.table(fnNE, header = TRUE, sep = "\t")
    NE <- merge(notEvaluated, data_stressInfo, by.x = "BMI_NotEvaluated", 
                by.y = "StdParamName", all.x = TRUE) %>%
      dplyr::select(Label)
    NE <- unlist(NE)
    bullet <- "\U2022"
  
    if (length(NE) > 0) {
      for (s in NE) {
        cat(paste0(bullet, " ", s, "\n\n"))
      }
    } else {
      cat("No stressors were eliminated from the evaluation.")
    }
    
  } else {
    cat(paste("The file", fnNE, "is not accessible."))
  }
} else {
  cat("Benthic macroinvertebrates were not evaluated.")
}

```

### **Weight of evidence**

#### *Detailed lines of evidence scores*

The table below displays the scores for each line of evidence by
stressor. Scores should be interpreted as described below for all lines
of evidence *except* for verified predictions using stressor-specific
tolerance values. This line of evidence relies on 8 components, and are
thus averaged.

-   1 (or a positive value) indicates that the line of evidence supports
    the stressor as a cause of impairment
-   -1 (or a negative value) indicates that the line of evidence refutes
    the stressor as a cause of impairment
-   0 indicates that the the line of evidence is indeterminate for the
    stressor as a cause of impairment
-   NE indicates that the line of evidence was not evaluated for the
    stressor

A note of caution:

-   Biological gradient assumes a linear relationship between stressor
    and response. A nonlinear relationship may be scored as
    indeterminate, even if it provides evidence for the candidate cause.
    We recommend viewing the biological gradient figures to corroborate
    the automated scoring.

```{r bmi_loe_bystressor, echo = FALSE}

if ("bmi" %in% biocommlist) { # BMI were evaluated
  
  fnLoEbyStressor <- paste0(TargetSiteID, "_LoEs.tab")
  fnLoEbyStressor <- file.path(dir_results, TargetSiteID, "BMI", "_WoE", 
                               fnLoEbyStressor)
  
  if (!file.exists(fnLoEbyStressor)) {# No WoE file
    
    txt_NoFile <- "No stressor-specific weight of evidence file is accessable.\n"
    cat(txt_NoFile)      
    
  } else {# WoE file exists
    
    dfLoEbyStressor <- read.table(fnLoEbyStressor, sep = "\t", na.strings = "NA",
                                  header = TRUE, strip.white = TRUE,
                                  stringsAsFactors = FALSE)
    dfLoEbyStressor <- dfLoEbyStressor %>%
      dplyr::mutate(Blank1 = NA) %>%
      dplyr::rename(BioGradIn = Gradient..inside., 
                    BioGradOut = Gradient..outside.) %>%
      dplyr::select(Stressor, StressSampleID, StressSampleDate, CO, Suff, 
                    BioGradIn, TS, VP_SSTV, VP_SSIbox, VP_SSIlog, Blank1, 
                    BioGradOut) %>%
      dplyr::arrange(Stressor, StressSampleDate)
    
    if (report_format == "html") {
      
      tblCaption <- paste0("<h5><strong>Detailed weight-of-evidence for each ",
                           "stressor and sample.</strong></h5>")
      cat(tblCaption)

      sketch <- htmltools::withTags(table(
        class = 'display',
        thead(
          tr(
            th(rowspan = 3, 'Stressor'),
            th(rowspan = 3, 'Sample ID'),
            th(rowspan = 3, 'Sample Date'),
            th(colspan = 7, 'Inside-the-Case'),
            th(rowspan = 3, ''),
            th(rowspan = 1, 'Outside the Case')
          ),
          tr(
            th(rowspan = 2, 'Co-Occurrence'),
            th(rowspan = 2, 'Sufficiency'),
            th(rowspan = 2, 'Biological Gradient'),
            th(rowspan = 2, 'Time Sequence'),
            th(colspan = 3, 'Verified Prediction'),
            th(rowspan = 2, 'Biological Gradient')
          ),
          tr(
            lapply(c('SSTolVals', 'SSI Co-Occurrence', 'SSI Sufficiency'), th)
          )
        )
      ))

      DT::datatable(dfLoEbyStressor,
                    # caption = tblCaption,
                    container = sketch,
                    extensions = 'FixedColumns',
                    class = 'striped hover row-border',
                    filter = 'none',
                    rownames = FALSE,
                    escape = FALSE,
                    options = list(layout = list(topStart = 'pageLength',
                                                 topEnd = 'search',
                                                 bottomStart = 'info',
                                                 bottomEne = 'paging'),
                                   # caption = list(captionSide = 'top',
                                   #                padding = '12px',
                                   #                fontWeight = 'bold'),
                                   pageLength = 10,
                                   bSort = FALSE,
                                   scrollX = TRUE,
                                   fixedColumns = list(leftColumns = 1),
                                   autoWidth = TRUE,
                                   menu = ifelse(nrow(dfLoEbyStressor) > 10,
                                                 c(10, 25, 50, 100), 10),
                                   columnDefs = list(#list(width = '280px',
                                                     #      targets = 0),
                                                     # list(width = '140px',
                                                     #      targets = 1),
                                                     # list(className = 'dt-left',
                                                     #      targets = 1:2),
                                                     # list(className = 'dt-head-center',
                                                     #      targets = 4:ncol(dfLoEbyStressor)),
                                                     # list(className = 'dt-center',
                                                     #      targets = 3:12),
                                                     list(className = 'dt-bottom',
                                                          targets = "_all")))) %>%
        DT::formatStyle(columns = colnames(dfLoEbyStressor), fontSize = '80%') %>%
        DT::formatStyle("StressSampleID", "white-space" = "nowrap")
      
    } else {
      
      msg <- "Not displayed in non-html format."
      cat(msg)
      
    }
    
  }
  
} else {
  cat("No benthic macroinvertebrate data.")
}

```

#### *Lines of evidence summary*

This table provides an indication of the consistency of the evidence for
a candidate cause. The strength of the evidence must also be considered.
For example, how well candidate causes explain biological responses in
the stressor-response analyses should also be evaluated.

```{r bmi_loecounts_bystressor, echo = FALSE}

if ("bmi" %in% biocommlist) { # BMI were evaluated
  
  fnLoESummary <- paste0(TargetSiteID, "_LoESummary.tab")
  fnLoESummary <- file.path(dir_results, TargetSiteID, "BMI", "_WoE", fnLoESummary)
  
  if (!file.exists(fnLoESummary)) {# No WoE file
    
    txt_NoFile <- "No stressor-specific weight of evidence file is accessable.\n"
    cat(txt_NoFile)      
    
  } else {# WoE file exists
    
    dfLoESummary <- read.table(fnLoESummary, sep = "\t", na.strings = "NA",
                                  header = TRUE, strip.white = TRUE,
                                  stringsAsFactors = FALSE)
    dfLoESummary <- dfLoESummary %>%
      dplyr::select(Stressor, StressSampleID, StressSampleDate, NumSupport,
                    NumRefute, NumIndeterminate, NumNotEvaluated) %>%
      dplyr::arrange(Stressor, StressSampleDate)
    
    if (report_format == "html") {
      
      tblCaption <- paste0("<h5><strong>Summary weight-of-evidence for each ",
                           "stressor and sample.</strong></h5>")
      cat(tblCaption)
      
      sketch <- htmltools::withTags(table(
        class = 'display',
        thead(
          tr(
            th('Stressor'),
            th('Sample ID'),
            th('Sample Date'),
            th('Supporting (>0)'),
            th('Refuting (<0)'),
            th('Indeterminate (=0)'),
            th('Not evaluated')
          )
        )
      ))

      DT::datatable(dfLoESummary,
                    # caption = tblCaption,
                    container = sketch,
                    extensions = 'FixedColumns',
                    class = 'striped hover row-border',
                    filter = 'none',
                    rownames = FALSE,
                    escape = FALSE,
                    options = list(layout = list(topStart = 'pageLength',
                                                 topEnd = 'search',
                                                 bottomStart = 'info',
                                                 bottomEne = 'paging'),
                                   # caption = list(captionSide = 'top',
                                   #                padding = '12px',
                                   #                fontWeight = 'bold'),
                                   pageLength = 10,
                                   bSort = FALSE,
                                   scrollX = TRUE,
                                   fixedColumns = list(leftColumns = 1),
                                   autoWidth = TRUE,
                                   menu = ifelse(nrow(dfLoESummary) > 10,
                                                 c(10, 25, 50, 100), 10),
                                   columnDefs = list(#list(width = '140px',
                                                     #      targets = 1),
                                                     # list(width = '140px',
                                                     #      targets = 2),
                                                     # list(className = 'dt-left',
                                                     #      targets = 1:2),
                                                     # list(className = 'dt-head-center',
                                                     #      targets = 4:ncol(dfLoESummary)),
                                                     # list(className = 'dt-center',
                                                     #      targets = 3:12),
                                                     list(className = 'dt-bottom',
                                                          targets = "_all")))) %>%
        DT::formatStyle(columns = colnames(dfLoESummary), fontSize = '80%') %>%
        DT::formatStyle("StressSampleID", "white-space" = "nowrap")
      
    } else {
      
      msg <- "Not displayed in non-html format."
      cat(msg)
      
    }
    
  }
  
} else {
  cat("No benthic macroinvertebrate data.")
}

```

### *Visuals for candidate causes*

The following images are lines of evidence graphics grouped by candidate
cause. Only the figures generated for the primary biotic index and
stressor-specific indices and tolerance values specified for inclusion
are displayed below. Figures for other indices are available in the
downloadable zip folder.

```{r bmi.LoE.graphics, echo = FALSE, out.width = "75%", fig.align = "left"}

stressors <- setdiff(siteDetects, NE)
paramName <- data_stressInfo$StdParamName[data_stressInfo$Label %in% stressors]
df.SSINames <- data_stressInfo[data_stressInfo$Label %in% stressors, ] %>%
  dplyr::filter(!is.na(SSIndex)) %>%
  dplyr::select(StdParamName, SSIndex)

dir.biocomm <- file.path(dir_results, TargetSiteID, "BMI")

msg_files <- paste0("All stressor graphics are in the '",
                    paste0(dir.biocomm, "/{stressor}"), "' folder.\n",
                    "Selected images are shown here.\n\n")
cat(msg_files)

for (s in seq_along(paramName)) {
  
  stressLabel <- stressors[s]
  stressName <- paramName[s]
  stressLabel <- sub("(mg/l)", "mg/L", stressLabel)
  stressLabel <- sub("(PCT)", "%", stressLabel)
  stressLabel <- sub("(u)g/m3", htmltools::HTML("\u00b5"), stressLabel)
  
  all.img <- list.files(file.path(dir.biocomm, stressName), pattern = ".png",
                        full.names = TRUE)

  cat(paste0("<br><h3><strong><em>", stressLabel, "</em></strong></h3>"))
  
  if (length(all.img) > 0) {
    
    if (length(all.img[grepl("CO.png$", all.img)]) == 1) {
      fn <- all.img[grep("CO.png$", all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nCo-occurrence image is not available.\n\n")
    }
    
    if (length(all.img[grepl("SU.png$", all.img)]) == 1) {
      fn <- all.img[grep("SU.png$", all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nSufficiency image is not available.\n\n")
    }
    
    if (length(all.img[grepl(paste0(bioIndex, "_GI.png$"), all.img)]) == 1) {
      fn <- all.img[grep(paste0(bioIndex, "_GI.png$"), all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nBiological gradient inside-the-case image is not available.\n\n")
    }
    
    if (length(all.img[grepl(paste0(bioIndex, "_GO.png$"), all.img)]) == 1) {
      fn <- all.img[grep(paste0(bioIndex, "_GO.png$"), all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nBiological gradient outside-the-case image is not available.\n\n")
    }
    
    # if (length(all.img[grepl(paste0(bioIndex, "_TS.png$"), all.img)]) == 1) {
    #   fn <- all.img[grep(paste0(bioIndex, "_TS.png$"), all.img)]
    #   cat(paste0("<img src='", fn, "'><br>"))
    # } else {
    #   cat("Time sequence image is not available.\n\n")
    # }
    
    if (length(all.img[grepl("VPSSTV.png$", all.img)]) == 1) {
      fn <- all.img[grep("VPSSTV.png$", all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nVerified predictions using stressor-specific tolerance values image is not available.\n\n")
    }
    
    if (length(all.img[grepl("VIbox.png$", all.img)]) == 1) {
      fn <- all.img[grep("VIbox.png$", all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nVerified predictions using stressor-specific indices box plot image is not available.\n\n")
    }
    
    if (length(all.img[grepl("VIreg.png$", all.img)]) == 1) {
      fn <- all.img[grep("VIreg.png$", all.img)]
      cat(paste0("<img src='", fn, "'><br>"))
    } else {
      cat("\nVerified predictions using stressor-specific indices logistic regression image is not available.\n\n")
    }
    
    cat("<br>")
    
  } else {
    msg_files <- paste0("No supporting image files exist for this stressor.\n\n")
    cat(msg_files)
  }##IF.img.length.START
  
}##FOR.stressors.loop

```
