---
title: "Plot Legend Key"
#subtitle: "CAST"
#author: "`r Sys.getenv('USERNAME')`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE, warning=FALSE)
#TargetSiteID <- "SRCKN001.61"
# dir_results <- "C:\\Users\\Erik.Leppo\\OneDrive - Tetra Tech, Inc\\MyDocs_OneDrive\\GitHub\\CASTfxn\\Results"
#~~~~~~~~~~~~~~~~~
# in global.R
dir_legends <- file.path(".", "data-raw", "Legends")
#~~~~~~~~~~~~~~~~~
# from getSiteInfo()
# data.Stations.Info
# data.cluster       <- data_Cluster_Hi
# col.clust.land.no <- "clust_noland"
# col.clust.land.yes <- "clust_land"
# all.map.sites <- merge(data.Stations.Info, data.cluster, by.x = "COMID_NHD2", by.y = "COMID")
#~~~~~~~~~~~~~~

# Legend Global Variables

## Plot margins
par(mar=c(5.1,4.1,4.1,2.1),mgp=c(3,1,0),las=0)

## Plot, Variables, Colors
col_outline       <- "black"
col_flowline      <- "light blue"
col_sites_all     <- "dark gray"
col_sites_all_ref <- "blue"
col_sites_cl      <- "cyan3"
col_sites_cl_ref  <- col_sites_all_ref
col_sites_ref     <- "blue"
col_sites_targ    <- "red"
col_outliers      <- "black"
col_line          <- "black"

## Plot, Variables, Fill
fill_sites_deg     <- "gray"
fill_sites_all     <- col_sites_all
fill_sites_all_ref <- fill_sites_all
fill_sites_ref     <- "white"
fill_sites_cl      <- col_sites_cl
fill_sites_cl_ref  <- fill_sites_cl 
fill_sites_targ    <- col_sites_targ
    
## Plot, Variables, Points    
pch_sites_all     <- 19 # solid circle
pch_sites_all_ref <- 21 # circle outline
pch_sites_cl      <- 19
pch_sites_cl_ref  <- pch_sites_all_ref
pch_sites_ref     <- 21 # circle outline 
pch_sites_targ    <- 17 # triangle
pch_sites_deg     <- 25 # Upside-down triangle
pch_outliers      <- 19

## Plot, Variables, Sizes
cex_all           <- 1.2
cex_mod           <- 1.5
cex_sites_all     <- 0.3 *2
cex_sites_all_ref <- cex_sites_all
cex_sites_ref     <- 0.9
cex_sites_cl      <- 1
cex_sites_cl_ref  <- cex_sites_cl
cex_sites_targ    <- 1.2
cex_outliers      <- 1

## Plot, Variables, Labels
txt_name         <- "Legend"
txt_outline      <- "Outline of SMC region"
txt_flowline     <- "NHD+ flow line"
txt_sites_all    <- "All sites"
txt_sites_deg    <- "Biologically degraded sites"
txt_sites_ref    <- "All reference sites (border around point)"
txt_sites_cl     <- "Non-reference sites in the same cluster as the Target site"
txt_sites_cl_ref <- "Reference sites in the same cluster as the Target site"
txt_sites_targ   <- "Target site"
txt_sites_obs    <- "Observed value"
txt_outliers     <- "Box plot outliers"
txt_line_fit     <- "Modeled fit"
txt_line_CI      <- "Modeled 75% prediction interval"
txt_line_caFit   <- "Comparator fit"
txt_line_caCI    <- "Comparator 75% prediction interval"
txt_line_targ    <- txt_sites_targ
txt_line_quant   <- "Quartiles"

## Plot, Variables, Lines
lwd_outline    <- 1.5
lwd_flowline   <- 0.5
lwd_all        <- 2.0
lwd_cl         <- 1.0
```

# Purpose
The various plots generated by the tool are shown below, by type, with a description of the major points.

## Disclaimer

The CAST is a Causal Assessment Screening Tool.  Its intended to assist the City and its agents to rapidly screen and identify the causes of biological impairment in a given waterbody, and thereby assist with prioritizing restoration and protection actions.  Due the CAST's reliance on currently available and sometimes incomplete data, however, it is not intended to be a final arbiter on causal assessments analyses, nor does it represent any commitments by the City to perform any specific projects, studies, or other actions.

## Box Plots, General
Box plots are used in many of the graphical representations of the data.  Below is the USGS standard key for box plots (https://owi.usgs.gov/blog/boxplots/).

Some box plots are rotated 90 degrees to allow for more values to be included on the plot.

Some box plots include additional points that are color coded.  These points are placed on the plot to show the distribution of select groups; e.g., reference, cluster, sites with better biological scores, target site, etc. The points are placed using the "jitter" command.  The jittering adds a small amount of random variation (x and y) to the location of the points so they are easier to visualize.  Thus the points should not be considered as exact locations and will be different each time the plots are generated.

```{r Leg_Box, echo=FALSE, eval=TRUE}
# USGS box plot legend
# https://github.com/usgs/wdfn-blog/blob/master/content/boxplot_defs.Rmd
# https://owi.usgs.gov/blog/boxplots/

library(ggplot2)
ggplot_box_legend <- function(family = "serif"){
  
  # Create data to use in the boxplot legend:
  set.seed(100)

  sample_df <- data.frame(parameter = "test",
                        values = sample(500))

  # Extend the top whisker a bit:
  sample_df$values[1:100] <- 701:800
  # Make sure there's only 1 lower outlier:
  sample_df$values[1] <- -350
  
  # Function to calculate important values:
  ggplot2_boxplot <- function(x){
  
    quartiles <- as.numeric(quantile(x, 
                                     probs = c(0.25, 0.5, 0.75)))
    
    names(quartiles) <- c("25th percentile", 
                          "50th percentile\n(median)",
                          "75th percentile")
    
    IQR <- diff(quartiles[c(1,3)])
  
    upper_whisker <- max(x[x < (quartiles[3] + 1.5 * IQR)])
    lower_whisker <- min(x[x > (quartiles[1] - 1.5 * IQR)])
      
    upper_dots <- x[x > (quartiles[3] + 1.5*IQR)]
    lower_dots <- x[x < (quartiles[1] - 1.5*IQR)]
  
    return(list("quartiles" = quartiles,
                "25th percentile" = as.numeric(quartiles[1]),
                "50th percentile\n(median)" = as.numeric(quartiles[2]),
                "75th percentile" = as.numeric(quartiles[3]),
                "IQR" = IQR,
                "upper_whisker" = upper_whisker,
                "lower_whisker" = lower_whisker,
                "upper_dots" = upper_dots,
                "lower_dots" = lower_dots))
  }
  
  # Get those values:
  ggplot_output <- ggplot2_boxplot(sample_df$values)
  
  # Lots of text in the legend, make it smaller and consistent font:
  update_geom_defaults("text", 
                     list(size = 3, 
                          hjust = 0,
                          family = family))
  # Labels don't inherit text:
  update_geom_defaults("label", 
                     list(size = 3, 
                          hjust = 0,
                          family = family))
  
  # Create the legend:
  # The main elements of the plot (the boxplot, error bars, and count)
  # are the easy part.
  # The text describing each of those takes a lot of fiddling to
  # get the location and style just right:
  explain_plot <- ggplot() +
    stat_boxplot(data = sample_df,
                 aes(x = parameter, y=values),
                 geom ='errorbar', width = 0.3) +
    geom_boxplot(data = sample_df,
                 aes(x = parameter, y=values), 
                 width = 0.3, fill = "lightgrey") +
    geom_text(aes(x = 1, y = 950, label = "500"), hjust = 0.5) +
    geom_text(aes(x = 1.17, y = 950,
                  label = "Number of values"),
              fontface = "bold", vjust = 0.4) +
    theme_minimal(base_size = 5, base_family = family) +
    geom_segment(aes(x = 2.3, xend = 2.3, 
                     y = ggplot_output[["25th percentile"]], 
                     yend = ggplot_output[["75th percentile"]])) +
    geom_segment(aes(x = 1.2, xend = 2.3, 
                     y = ggplot_output[["25th percentile"]], 
                     yend = ggplot_output[["25th percentile"]])) +
    geom_segment(aes(x = 1.2, xend = 2.3, 
                     y = ggplot_output[["75th percentile"]], 
                     yend = ggplot_output[["75th percentile"]])) +
    geom_text(aes(x = 2.4, y = ggplot_output[["50th percentile\n(median)"]]), 
              label = "Interquartile\nrange", fontface = "bold",
              vjust = 0.4) +
    geom_text(aes(x = c(1.17,1.17), 
                  y = c(ggplot_output[["upper_whisker"]],
                        ggplot_output[["lower_whisker"]]), 
                  label = c("Largest value within 1.5 times\ninterquartile range above\n75th percentile",
                            "Smallest value within 1.5 times\ninterquartile range below\n25th percentile")),
                  fontface = "bold", vjust = 0.9) +
    geom_text(aes(x = c(1.17), 
                  y =  ggplot_output[["lower_dots"]], 
                  label = "Outside value"), 
              vjust = 0.5, fontface = "bold") +
    geom_text(aes(x = c(1.9), 
                  y =  ggplot_output[["lower_dots"]], 
                  label = "-Value is >1.5 times and"), 
              vjust = 0.5) +
    geom_text(aes(x = 1.17, 
                  y = ggplot_output[["lower_dots"]], 
                  label = "<3 times the interquartile range\nbeyond either end of the box"), 
              vjust = 1.5) +
    geom_label(aes(x = 1.17, y = ggplot_output[["quartiles"]], 
                  label = names(ggplot_output[["quartiles"]])),
              vjust = c(0.4,0.85,0.4), 
              fill = "white", label.size = 0) +
    ylab("") + xlab("") +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank(),
          aspect.ratio = 4/3,
          plot.title = element_text(hjust = 0.5, size = 10)) +
    coord_cartesian(xlim = c(1.4,3.1), ylim = c(-600, 900)) +
    labs(title = "EXPLANATION")

  return(explain_plot) 
  
}

ggplot_box_legend()
```

## Site Info

### Map, Static
The static map displays all sites in entire region of interest alont with NHD+ flowlines.

All sites (gray), comparator sites (light blue), and target site (red) are ploted on the map.  Reference sites are marked with a dark blue outline.

```{r Map_Static}
str_cat <- "static map"
dir.sub3 <- "SiteInfo"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3, paste0(TargetSiteID,"_map.jpg"))
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
}
#~~~~~~~~~~~~~~~~

# Key

# https://stackoverflow.com/questions/48966645/how-can-i-create-a-legend-without-a-plot-in-r

## Plot, Variables, Legend
leg_name   <- txt_name
leg_labels <- c(txt_outline, txt_flowline, txt_sites_all, txt_sites_cl, txt_sites_ref, txt_sites_targ)
leg_shape  <- c(rep(NA,2), pch_sites_all, pch_sites_cl, pch_sites_ref, pch_sites_targ)
leg_size   <- cex_mod * c(NA, NA, cex_sites_all, cex_sites_ref, cex_sites_cl, cex_sites_targ)
leg_line   <- c(1, 1, rep(NA, 4))
leg_lineWd <- c(1, 1, rep(NA, 4))
leg_col    <- c(col_outline, col_flowline, col_sites_all, col_sites_cl, col_sites_ref, col_sites_targ)
leg_fill   <- c(rep(NA,2), fill_sites_all_ref, fill_sites_cl, fill_sites_ref, fill_sites_targ)

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 1)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
```

### Map, Interactive
The interactive map behaves much like Google Earth.

The points have the same color coding as the static map.

```{r Map_Leaflet}
str_cat <- "interactive map"
dir.sub3 <- "SiteInfo"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3, paste0(TargetSiteID, "_map_leaflet.png"))
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  #print(paste0("\n", fn_img))
}

# Legend plot is the same as the static map
```

### Potential Anthropogenic Alteration Plots
Bar plots for target site with metrics from StreamCat.  Most plots have panels or facets that subdivide the data into categories. The numbers above the bars is the value of the bar.

The color of the bars is a shade of red to associated it with the "target" site.

No scoring of data from these plots.

```{r PotAnthAlt}
str_cat <- "potential anthropogenic alterations"
dir.sub3 <- "SiteInfo"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3, paste0(TargetSiteID, "_bkgd_RoadDensity.png"))
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name <- txt_name
leg_labels <- c(txt_sites_obs)
leg_shape  <- c(NA)
leg_size   <- cex_mod * c(1)
leg_line   <- c(1)
leg_lineWd <- c(10)
leg_col    <- c("dark red")
leg_fill   <- c(NA)

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 1)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
```

## Candidate Causes

Box plots by parameter.

Comparator sites values for non-degraded biological scores are points on the plot.  The target site is a red triangle.

No scoring of data from these plots.

```{r CandCaus}
str_cat <- "candidate causes"
dir.sub3 <- "CandidateCauses"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3, paste0(TargetSiteID, ".boxes.Water.quality.jpg"))
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name   <- txt_name
leg_labels <- c(txt_outliers, txt_sites_cl_ref, txt_sites_targ)
leg_shape  <- c(pch_outliers, pch_sites_ref, pch_sites_targ)
leg_size   <- cex_mod * c(cex_outliers, cex_sites_ref, cex_sites_targ)
leg_line   <- c(NA)
leg_lineWd <- c(NA)
leg_col    <- c(col_outliers, col_sites_ref, col_sites_targ)
leg_fill   <- c(col_outliers, col_sites_cl, col_sites_targ)

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 1)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
```

## CoOccurrence

### Box Plot
Box plot of specific conductivity.

Scoring based on the 50th and either the upper (75th) or lower (25th) quartile of the distribution of parameter values of comparator sites.

The score lines are black dotted lines and the target site value is the thicker dashed red line.  Between the black lines is a score of 0.  Values outside of the lines are scored as 1 or -1 depending on the expected direction of the parameters response to increasing perturbation.

Only comparator sites with higher biological scores are included on the plot.  The points have been grouped as degraded and non-degraded.

```{r CO_box}
str_cat <- "co-occurrence, box plot"
dir.sub3 <- "CoOccurrence"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3
                    , paste0(TargetSiteID, ".CoOccurrence.Box.SpecificConductivity_fld_uS_cm.jpg"))
if(file.exists(fn_img)){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name <- txt_name
leg_labels <- c(txt_outliers, txt_sites_cl_ref, txt_sites_cl, txt_sites_targ, txt_line_quant)
leg_shape  <- c(pch_outliers, pch_sites_ref, pch_sites_deg, rep(NA,2))
leg_size   <- cex_mod * c(cex_outliers, cex_sites_ref, cex_sites_cl, rep(NA,2))
leg_line   <- c(rep(NA,3), 2, 2)
leg_lineWd <- c(rep(NA,3), 2, 1)
leg_col    <- c(col_outliers, col_sites_all_ref, col_sites_all, 2, 1)
leg_fill   <- c(col_outliers, col_flowline, fill_sites_deg, rep(NA,2))

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 0.7)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)

# Red line = target site
# points are cluster sites marked as biologically degraded Yes/No.
# Biologically Degraded = No are the "better" sites.
# N and score in text at the bottom.
```

### Stressor Response Curve
Stressor-response of parameter of interest.

Scoring based on the 50th and 20th quartiles of the distribution of parameter values of comparator sites with measured values for the parameter of interest and CSCI scores.

The score lines are black dotted lines and the target site value is the thicker dashed red line.  The red dashed line indicates where the target site parameter value is to be placed on the blue curve.    Values between the black lines is a score of 0.  Values outside of the lines are scored as 1 or -1 depending on the expected direction of the parameters response to increasing perturbation.

```{r CO_SR}
str_cat <- "co-occurrence, stressor response"
dir.sub3 <- "CoOccurrence"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3
                    , paste0(TargetSiteID, ".CoOccurrence.SR.SpecificConductivity_fld_uS_cm.jpg"))
if(file.exists(fn_img)==TRUE){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name   <- txt_name
leg_labels <- c(txt_sites_ref, txt_sites_deg, txt_line_fit, txt_line_targ, txt_line_quant)
leg_shape  <- c(pch_sites_ref, pch_sites_deg, rep(NA,3))
leg_size   <- cex_mod * c(cex_sites_ref, cex_sites_cl, rep(NA,3))
leg_line   <- c(rep(NA,2), 1, 2, 2)
leg_lineWd <- c(rep(NA,2), 2, 2, 1)
leg_col    <- c(col_sites_all_ref, col_sites_all, 4, 2, 1)
leg_fill   <- c(col_flowline, fill_sites_deg, rep(NA,3))

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 0.7)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
```

## Stressor-Response

Scattplot with linear regression fit and 75% prediction interval.

Several layers of data are overlaid on this plot of the biological value and parameter of interest. 

The target site is a red triangle.  All sites are denoted as gray points.  Comparator sites are a lighter blue color.  Any samples with biological scores of non-degraded are notes with a dark blue outline.

The lines represent the linear regression fit with 75th prediction intervals.  The lines in black are using all sites. The lines in the lighter blue represent the same analysis with only comparator sites.

The regression lines, r-square values, number of records, and scores are shown below the plots.

**NEED SCORING TEXT**

```{r SR}
str_cat <- "Stressor-Response, scatter plot"
dir.sub3 <- "StressorResponse"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3
                    , paste0(TargetSiteID, ".SR.BMI.SpecificConductivity_fld_uS_cm_CSCI.jpg"))
if(file.exists(fn_img)){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name <- txt_name
leg_labels <- c(txt_sites_all, txt_sites_ref, txt_sites_cl, txt_sites_cl_ref, txt_sites_targ, txt_line_fit, txt_line_CI, txt_line_caFit, txt_line_caCI)
leg_shape  <- c(pch_sites_all, pch_sites_all_ref, pch_sites_cl, pch_sites_cl_ref, pch_sites_targ, rep(NA,4))
leg_size   <- cex_mod * c(cex_sites_all, cex_sites_ref, cex_sites_cl, cex_sites_cl_ref, cex_sites_targ, rep(NA,4))
leg_line   <- c(rep(NA,5), 1, 2, 1, 2)
leg_lineWd <- c(rep(NA,5), 3, 3, 1, 1)
leg_col    <- c(col_sites_all, col_sites_ref, col_sites_cl, col_sites_cl_ref, col_sites_targ, col_line, col_line, col_sites_cl, col_sites_cl)
leg_fill   <- c(fill_sites_all_ref, fill_sites_all_ref, fill_sites_cl, fill_sites_cl_ref, fill_sites_targ, rep(NA,4))

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 1)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
````

## Time Sequence

Bar plots of values vs. time.

Plots are intended to aid the user in visualizing the relative sampling time frames of the biological sample and parameter of interest.

Values for the parameter of interest and biological scores are represented by the height of the bars.

No scoring of data from these plots.

```{r TimeSeries}
str_cat <- "TimeSequence, bar plot"
dir.sub3 <- "TimeSequence"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3
                    , paste0(TargetSiteID, ".TS.SpecificConductivity_fld_uS_cm.CSCI.jpg"))
if(file.exists(fn_img)){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name <- txt_name
leg_labels <- c(txt_sites_obs)
leg_shape  <- c(NA)
leg_size   <- cex_mod * c(1)
leg_line   <- c(1)
leg_lineWd <- c(10)
leg_col    <- c(1)
leg_fill   <- c(NA)

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 1)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
````

## Verified Predictions

Box plots of relative abundance, by taxa grouping.  Taxa groupings are taxa considered tolerant or intolerant to the parameter of interest.

Only samples with better biological scores than the target site are used to generate the plot.

Site biological scores  are classified as either degraded or not degraded.

Scoring based on the 50th and either the upper (75th) or lower (25th) quartile of the distribution of the relative abundance of taxa groupings in teh samples from comparator sites.

The score lines are black dotted lines and the target site value is the thicker dashed red line.  Values between the black lines is a score of 0.  Values outside of the lines are scored as 1 or -1 depending on the expected direction of the parameters response to increasing perturbation.

```{r Verified}
str_cat <- "Verified Predictions, box plot"
dir.sub3 <- "VerifiedPredictions"
TargetSiteID <- "403S01784"
fn_img <- file.path(".", dir.sub3
                    , paste0(TargetSiteID, ".SR.SSTV.SpecificConductivity_fld_uS_cm.jpg"))
if(file.exists(fn_img)){
  knitr::include_graphics(fn_img)
} else {
  print(paste0("No file exists; ", str_cat))
  # print(paste0("\n", fn_img))
}
#~~~~~~~~~~~~~~~~

# Key

## Plot, Variables, Legend
leg_name   <- txt_name
leg_labels <- c(txt_outliers, txt_sites_cl_ref, txt_sites_targ, txt_line_quant)
leg_shape  <- c(pch_outliers, pch_sites_all_ref, rep(NA,2))
leg_size   <- cex_mod * c(cex_outliers, cex_sites_ref, cex_sites_cl, cex_sites_targ)
leg_line   <- c(rep(NA,2), 2, 2)
leg_lineWd <- c(rep(NA,2), 2, 2)
leg_col    <- c(col_outliers, col_sites_ref, col_sites_targ, col_line)
leg_fill   <- c(col_outliers, col_flowline, col_sites_targ, col_line)

plot(NULL, xaxt = "n", yaxt="n", bty="n", xlab="", ylab="", xlim=0:1, ylim=0:1)
legend("topleft"
       , legend = leg_labels
       , pch = leg_shape
       , pt.cex = leg_size
       , col = leg_col
       , pt.bg = adjustcolor(leg_fill, alpha = 0.7)
			 , lty = leg_line
			 , lwd = leg_lineWd
       , cex = cex_all
       , bty = "n"
       # , title = ""
       )
mtext(leg_name, at=0.05, cex = 2)
````
